### 2019-10-18 manuscript.tex
Updates from Overleaf

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{upgreek}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{subfig}
\usepackage[version=4]{mhchem}
\onehalfspacing
\graphicspath{figures/}

\title{Carbon cathodes for rechargeable aluminium-ion batteries}

\author{
  Shalini Divya\\
  School of Chemical and Physial Sciences\\
  Victoria University of Wellington\\
  Wellington, New Zealand\\
  \texttt{shalini.divya@vuw.ac.nz}\\
  %% examples of more authors
   \And
  Thomas Nann\thanks{Corresponding author.}\\
  School of Mathematical and Chemical Sciences\\
  The University of Newcastle\\
  Newcastle, NSW 2308, Australia\\
  \texttt{thomas.nann@newcastle.edu.au}\\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
\maketitle
\begin{abstract}
 In this work, we compare four different forms of carbon: activated carbon from human hair (ACH), hemp fibers, a fullerene extract (CFEx) and Super-P carbon black as cathodes for non-aqueous aluminium-ion batteries. These materials differ in their general structure, porosity and morphology. The fullerenes display a crystalline structure, whereas hemp fibers, Super-P and ACH are amorphous in nature. Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^-{^1}$ with a coulombic efficiency of ~90\% at a current rate of 50 mV s$^-{^1}$. Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^-{^1}$ respectively. CFEx, a mixture of \ce{C60} (85\%) and \ce{C70} (15\%) fullerene, recorded its highest capacity at 78 mAh g$^-{^1}$ and maintained it for 50 cycles. The cells were charged and discharged to 2.45 V and 0.2 V respectively. \end{abstract}
% keywords can be removed
\keywords{carbon-based cathodes \and aluminium-ion battery \and ionic liquid \and human hair \and fullerene extract \and hemp fibers \and Super-P}
\section{Introduction}
Different varieties of carbon-based materials have been widely used in energy storage applications. Graphite, with its layered structure turned out to be an ideal intercalation cathode \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}. Activated carbon, owing to its porous structure, provided a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}. Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and aim to provide higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium. Exhaustive use of lithium and cobalt in LIBs would make portable batteries expensive in the coming years. One needs to switch to cost-effective alternatives. The above-mentioned properties make AIBs an interesting alternative\cite{ambroz_trends_2017-1}. We tested a number of rechargeable AIBs using an ionic liquid electrolyte with carbon-based cathodes.
Graphite has been commonly used as a cathode in AIBs. It has a) a layered structure that enhances the intercalation process, b) good conductivity and c) a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V. Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, which showed specific capacities ranging from 60-250 mAh g$^-^1$. The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge. X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism\cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}. Raman data showed that conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicated two stages of intercalation. XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively\cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/graphitemech}
    \caption{Intercalation of AlCl$_4^_$ ions while cell charging and deintercalation during discharge in a \textbf{Al/graphite} cell. The interlayer distance between two graphite sheets is 3.3 $\AA$.}
  \label{SF:graphitemech}
\end{figure}
In this study, we compared four carbon-based materials with carbonised natural products. Super-P carbon has been used consistently as an additive to overcome any conductivity loss an active material suffers when a polymer binder such as PVDF, is added to it. Using it as an active material, we tried to find if Super-P contributes any capacity of its own to the battery's specific capacity. Activated carbon from natural products like rice or wood have been previously used in super-capacitors\cite{hussain_development_2019, frackowiak_carbon_2001}. Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes . The pores absorb the charge carriers reversibly on their surface. Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes and got some interesting results. 
\section{Results and discussion}
\begin{table}[tbh!]
\caption{Comparing average battery metrics of all carbon cathodes} \label{table1}
\begin{threeparttable}
\begin{center}
\begin{tabular}{lcccc}
\headrow
\hline
\thead{Active material} & \thead{\textbf{Size (pore size)}} & \thead\textbf{Specific capacity (mAh g$^-^1$)} & \thead\textbf{Cell efficiency (\%)} & \thead{\textbf{Cell voltage (V)}}\\
\hline
Activated carbon from human hair & 5\mu m & 102 & 97 & 1.9 \\
Fullerene extract & 8.8\AA & 78 & 85 & 1.7 \\
Hemp fibers & 2.3 \mu m & 49 & 75 & 1.8 \\
Super-P & 300\AA & 46 & 40 & 1.5 \\
\hline  % Please only put a hline at the end of the table
\end{tabular}
\end{center}

%\begin{tablenotes}
%\item JKL, just keep laughing; MN, merry noise.
%\end{tablenotes}
\end{threeparttable}
\end{table}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CDCall}
    \caption{Specific capacities in the a) 1$^s^t$ and b) 50$^t^h$ cycle of ACH, hemp fibers, CFEx and Super-P cathodes at a current rate of 50 mA g$^-{^1}$. c) Cell efficiencies of cells at a current rate of 50 mAg$^-^1$. d) Specific capacities of carbon cells at current rates of 25 mAg$^-^1$, 50 mAg$^-^1$ and 100 mAg$^-^1$ in a two-electrode setup against \ce{Al^{3+}}/Al. }
  \label{figures:CDCall}
\end{figure}
Our battery system comprised of a cathode, 99\% pure aluminium foil as an anode and a room temperature ionic liquid (RTIL) acting as the electrolyte. ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra showed presence of a few graphitic planes. Any number of graphite-like layers would allow \ce{AlCl4-} ions to intercalate when the cell was charged. However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had a crystalline lattice. Intercalation into the fullerene cage was not feasible because it needed a high amount of energy to break a C-C bond. We suggest that \ce{AlCl4-} anions seeped through the gaps present in between fullerenes without altering the molecular structure. Using a Neware BTS 3000 battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^-^1$ in Figure\ref{figures:CDCall}a and b. Structural changes in the cathode before and after cycles was studied using their Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.
ACH cells recorded the highest capacity at 102-mAh g$^-{^1}$ and maintained it for 50 cycles. Coulombic efficiency was stable at ~95$\%$. Porous structure gave the material a high surface area that lead to an additional surface-based charge storage mechanism (observed in capacitors).Hemp fibers, due to their porous structure, observed a similar mechanism. Hemp cell showed a capacity of 56 mAh g$^-{^1}$ in its first cycle, which decreased to 45 mAh g$^-{^1}$ after 50 cycles. 
CFEx cell recorded its first discharge capacity at 79 mAh g$^-{^1}$, which shifted to just 78 mAh g$^-{^1}$. The cell maintained its coulombic efficiency at ~90$\%$. 
Specific capacity of the Super-P cell decreased considerably after repeated charge/ discharge cycles. With an initial capacity of 84 mAh g$^-^1$, the value decreased to 47 mAh g$^-{^1}$ with a low coulombic efficiency of $\sim$40$\%$. 
A low coulombic efficiency, which was also observed in the hemp cell, can be attributed to degradation of cathode structure, also known as cathode pulverisation. It seems due to continuous cycling, weak bonds existing between sections of the cathode broke and agglomerated into smaller chunks of C atoms. As a result, the number of surface pores decreased, which reduced the cell's capacity (Figure \ref{figures:CDCall}c). 
Human hair has two components- cuticle and cortex. One way to make carbon porous is by treating it with an activating agent. Using activating agents especially alkali hydroxides improves the porosity and increases the surface area of material \cite{liu_hair-based_2017} .
In this work, sodium hydroxide (NaOH) was used as the activating agent, which breaks the weak interactions existing between the overlapping cells in the cortex. The reaction that takes place inside the matrix after adding NaOH is:
\begin{center}
    \\4NaOH + C \longrightarrow 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{qian_human_2013}
\end{center}

NaOH was reduced to Na, these atoms in turn expanded the carbon matrix. Oxidation of carbon formed \ce{CO2}, which created pores. An increase in temperature lead to Na activation, which was later removed from the matrix via channels created by \ce{CO2}. The channels created in this process provided path for \ce {AlCl4-} to intercalate inside the pores. The activating agent:carbon ratio and the calcinating temperature played an important role in determining the size of pores. The calcinating temperature used here was 750$^{\circ}$C. A schematic of ACH synthesis has been described in Figure \ref{SF:ACHsyn}. Dong \textit{et al.} suggested that at higher temperatures (>900$^{\circ}$C) pores start to collapse resulting in graphitic sheets \cite{dong_commercial_2019}. 
Fibers obtained from Hemp (\textit{Cannabis Sativa L.}) have been used in several commercial items including paper, textiles, clothing, biodegradable plastics, paints, and bio-fuels. They have been used as reinforcements in composite materials and are capable of replacing glass fibers. Hemp fibers have a high moisture content which can be removed after high temperature treatment\cite{hussain_development_2019}. For creating activated carbon from these fibers, potassium hydroxide (KOH) was used as the activating agent. Since the samples were obtained from Carbon Valley\textsuperscript{\textregistered}, we are unable to report the precise calcinating temperature used. Unfortunately the structural domains appeared to have been damaged after this process. This phenomena negatively impacted its charge-storing capacity.  
Fullerenes have a fused-ring structure. The nucleus-to-nucleus diameter is 7.1\AA\ and van der Waals diameter is 11\AA\ in a single crystal. Presence of $\pi$-electrons on its surface makes it a good electron acceptor. However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity\cite{loutfy_fullerene_2002, winkler_two-component_2007}. Electrochemical reduction of \ce{C60} to \ce{C60^{-3}} is highly reversible suggesting they are capable of giving reversible capacities. However, they are weak battery cathode materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}. To test their solubility in \ce{AlCl3}-EMImCl ionic liquid, 100 mg of CFEx was mixed in the electrolyte and stirred for 4 hours. For comparison, we mixed hemp fibers in another vial. The vials were left to stand for 24 hours in a \ce{N2}-filled glove box. A phase separation was observed with hemp fibers but not for CFEx indicating it dissolved in the electrolyte (Figure \ref{SF:CFExsol}. It has been reported in Li-S batteries that poly-sulphides produced during charge-discharge were soluble in the electrolyte. It forms an insulating layer of \ce{Li2S} on the anode, which resulted in capacity fading \cite{sun_effect_2017, yan_2d_nodate}. However, reversible capacities obtained after 50 cycles suggested no such molecules were formed with \ce{AlCl3}/EmImCl electrolyte. 
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/superPmech}
    \caption{Suggested mechanism for a \textbf{Al/Super-P} cell. Super-P has a very amorphous structure with a few graphite-like planes present in it. AlCl$_4^_$ ions intercalate into those layers and give the cell its capacity. However, cathode pulverisation results in capacity fading.}
  \label{figures:superPmech}
\end{figure}
Pore size for Super-P ranges from ~30-50 nm \cite{younesi_analysis_2015}. It has the least graphitic structure when compared to ACH and hemp fibers. Loosely held structures, which disintegrated rapidly after every cycle resulted in reduced capacity and low coulombic efficiency values.

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/hempmech}
    \caption{Suggested mechanism for a \textbf{Al/hemp} cell. The fibers have a large pore size (2.0-2.5 \mu m) which allow the AlCl$_4^_$ to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
  \label{figures:hempmech}
\end{figure}
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/raman}
    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx , b) hemp fibers, c) ACH and d) Super-P cathodes indicating presence of both D and G-bands.}
  \label{figures:raman}
\end{figure}
Since it has been previously established that intercalation of \ce{AlCl4-} takes place in carbon materials during cell charge, we focused our analysis on the charged electrodes. Figure \ref{figures:raman} illustrates Raman spectra of the tested cathodes. Pristine ACH, hemp fibers and Super-P had a significant D-band indicating a distorted lattice. Increased intensity of D band can be seen in charged electrodes at ~1300 cm$^-{^1}$ (ACH), 1329.7 cm$^-{^1}$ (hemp fibers), and 1352.0 cm$^-{^1}$ (Super-P) indicating an increase in the lattice defects and deformities. Hemp fibers and ACH observed an increased FWHM (full width at half maximum) of both D and G bands indicating a loss in symmetry. Intercalation of ions or surface adsorption of anions onto the porous carbon cathode, would alter the ordered structure on the surface. We suggest capacitive intercalation mechanism as well as a redox pseudocapacitance where \ce{AlCl4-} ions electrochemically adsorb onto the surface \cite{brezesinski_ordered_2010}. 
The main feature in a fullerene Raman spectrum was a sharp line observed at 1460 cm$^-^1$, which is known as the 'pentagonal pinch mode'. \ce{C60} is composed of \ce{sp2} bonded carbon atoms. Sharpness of the band indicates a uniform nature of the bonds. However, the spectrum of C$_7_0$ has multiple bands. Reduction in its molecular symmetry increases the number of active Raman bands \cite{kimbrell_analysis_2014}. Pristine CFEx electrode observed characteristic peaks of both \ce{C60} and \ce{C70} at 1459.3 cm$^-{^1}$ and 1564 cm$^-{^1}$ respectively in Figure \ref{figures:raman}c. An interesting observation was that pristine and charged CFEx electrodes had a similar-looking spectra after cycling. Since Raman spectroscopy is sensitive to very minute differences in molecular morphology, the results suggested that the structure remained intact. Another interesting observation was made in charged ACH electrode (Figure \ref{figures:raman}a). A new peak appeared at 1466 cm$^-{^1}$. A similar band splitting was observed by Wang \textit{et al} \cite{wang_kish_2017} while charging natural graphite and AlCl$_4^-$ ions intercalated into the cathode layers. This peak appeared due to vibration of carbon atoms in a plane adjacent to intercalant layer planes. We observed no such effect was observed for any other cathode. Since the Al/ACH cell maintained a highly reversible capacity of 102 mAhg$^-^1$ after 50 cycles, we assume ACH underwent a similar mechanism, where \ce{AlCl4-} ions intercalate into the cathode during charge. ACH has a high surface area and an inter-connected mesoporosity. The layered domains present in it enable insertion of \ce{AlCl4-}, while a few anions get electrochemically adsorbed onto the surface through a charge-transfer process resulting in a redox pseudo-capacitance. All these processes seem to take place at the same time without changing the reaction kinetics. Additionally, presence of both an amorphous and crystalline structure in this material increases the charge-storage capacity of the material \cite{brezesinski_ordered_2010}. This might be the reason why ACH shows a remarkable reversibility. Schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}. Hemp fibers and Super-P had lattice deformities to begin with, which were enhanced after the cell underwent the preliminary galvanostatic cycles. This decreased capacity after every cycle. 
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/SEM}
    \caption{Scanning electron microscopy images comparing pristine a) ACH, b) hemp fibers, c) CFEx and d) Super-P; and charged e)ACH, f) hemp fibers, g) CFEx and h) Super-P electrodes. Hemp fibers and Super-P undergo prominent changes after charge/discharge cycles (visible agglomeration of carbon atoms).}
  \label{figures:SEM}
\end{figure}
Above results seem to be in good agreement with SEM images in Figure 9, where we compared pristine (Figure \ref{figures:SEM}a, b, c and d) and charged electrodes (\ref{figures:SEM}e,f,g and h). ACH and hemp fibres have a porous structure (Figure \ref{figures:SEM}a and 9b), which looked visibly degraded after cycles (Figure \ref{figures:SEM}e and f). Agglomeration of carbon atoms increases the edge defects in a material. This explains the high intensity of D-bands of these cathodes, Figure \ref{figures:raman}. Surface morphology of CFEx (Figure \ref{figures:SEM}c did not change a lot after charge (Figure \ref{figures:SEM}g), similar to our observations in its Raman spectra. 
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/XRD}
    \caption{XRD spectra comparing a pristine (black), charged (green) and discharged (red) a) CFEx and b)ACH cathode to study changes in their lattice after 50 galvanostatic cycles in a two-electrode setup against \ce{Al3+}/Al with characteristic peaks marked for \ce{C60} (in grey) and \ce{C70} (in blue).}
  \label{figures:XRD}
\end{figure}
To confirm the reversible electrochemical processes taking place in CFEx and ACH, we examined their XRD spectra (pristine, charged and discharged) in Figure \ref{figures:XRD}a and b respectively. Pristine cathode recorded the characteristic peaks of both \ce{C60} and \ce{C70}, which reappeared after discharge suggesting a reversible process. However, charged electrode observed new diffraction peaks which can be attributed to lattice deformities taking place at the electrode/electrolyte interface. We calculated the unit cell lattice parameters for both pristine and charged cathode for a \ce{C60} molecule. The unit cell had a tetragonal crystal system with space group of P42/mmc and a space group number 131 (ICDD: 04-013-1339 for \ce{C60}). Lattice parameter 'a' and 'b' for the charged electrode changed from 9.06\AA to 9.57\AA . Lattice parameter 'c' changed from 15.03\AA to 15.65\AA, in Figure \ref{figures:CFExcryst}a and b. Lattice parameters for discharged cathode were closer to pristine values. The changes in the fullerene structure suggested a reversible intercalation process taking place, where the unit cells shifted from their original location during charge and returned back after discharge. A possible site for \ce{AlCl4-} intercalation is depicted in Figure \ref{figures:CFExcryst}c. XRD spectra for ACH electrodes was inconclusive (Figure \ref{figures:XRD}b). Pristine cathode observed very broad peaks suggesting the extreme amorphous nature of the material. However, the material seemed to have a more ordered structure after the galvanostatic cycles. It seems that surface-based charge-storage was more dominant than the intercalation process. This is why presence of crystallinity in the active material does not limit the surface-based charge storage and therefore, the capacity remains same \cite{kim_synthesis_2006, jow_factors_2018}. 
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/ACHmech}
    \caption{Suggested mechanism for a \textbf{Al/ACH} cell. ACH has a porous structure which allows AlCl$_4^_$ ions to get absorbed as well as reversibly intercalate into the graphitic planes, giving additional capacity to the cell.}
  \label{figures:ACHmech}
\end{figure}

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CFExcryst}
    \caption{Changes in the lattice parameters of a \ce{C60} unit cell. a) Pristine \ce{C60}unit cell, b) charged \ce{C60}unit cell with increased parameters suggesting a uniform shift in the lattice after charge/discharge. c) Expected intercalation sites of \ce{AlCl4-} ions in the unit cell.}
  \label{figures:CFExcryst}
\end{figure}
%Charged Super-P and hemp fiber electrodes underwent degradation and appeared clumped together resulting in capacity decay. This was visible from their electrochemical results where a rapid decrease in capacity and cell efficiency was noted. 
%XPS analysis results... C 1s 
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/XPSC}
    \caption{Carbon 1s XPS spectra of pristine a) ACH, b) Super-P, c) hemp fibers and d) CFEx cathodes.While ACH, Super-P and hemp fibers observe carbonyl functional groups, CFEx cathodes have symmetrical looking $\pi$* and $\sigma$* satellite peaks.}
  \label{figures:XPSC}
\end{figure}
We performed X-ray photoelectron spectroscopy on our cathodes to understand the kinds of reactions the cathodes could take part in. We observed ACH, hemp fibers and Super-P had similar looking peaks for carbon 1s orbital, Figure \ref{figures:XPSC}. Peaks for sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds (formed between PVDF and the active material) appeared for ACH, hemp fibers and Super-P cathodes. To understand the presence of these bonds,we looked into the composition of these active materials. Hair is mainly composed of a protein called keratin displayed in Figure \ref{SF:keratin}. Keratin constitutes of various C-H, C=O, C-OH and C-NH$_2$ bonds with their respective binding energies as observed in Figure \ref{figures:XPSC}a. Sulphur is an essential part of this protein, a C-S bond can be observed at 286.94 eV (blue peak). 
\begin{table}
\caption{XPS data sheet for the tested cathodes with \textbf{Carbon 1s} peaks pointing C-H/ C-C, C-O/ C-OH, C=O/ O-C=O and C-F bonds, \textbf{Nitrogen 1s} peaks for pyrrolic and pyridnic N nods and \textbf{Oxygen 1s} peaks for aliphatic C-O and aromatic C=O peaks.} \label{table2}
\begin{tabular}{cccccccc}
\hline
\thead {Active} & \thead{C-H/} & \thead{C-O/} & \thead{C=O/} & \thead{C-F} & \thead{Pyrrolic N/} & \thead{aliphatic C-O} & \thead{aromatic C=O}\\
\thead {material} & \thead{C-C} & \thead{C-OH} & \thead{O-C=O} & \thead{} & \thead{Pyridinic N} & \thead{} & \thead{}\\
\hline\\
ACH & 284.5 eV & 285.8 eV & 288.4 eV & 290.2 eV & 400.2 eV/ & 533.0 eV & 531.2 eV\\
& & & & & 398.3 eV & & \\
CFEx & 284.2 eV & 286.0 eV & 288.2 eV & 290.0 eV & 399.3 eV & 531.3 eV & 530.2 eV\\
Hemp fibers & 284.5 eV & 286.0 eV & 288.7 eV & 290.5 eV & 400.3 eV & 532.9 eV & 531.4 eV\\
Super-P & 284.3 eV & 286.7 eV & 288.0 eV & 290.7 eV & 400.2 eV & 532.8 eV & ---\\
\hline
\end{tabular}
\end{table}
The oxygen-containing carbonyl and ester groups improve the wettability of cathode materials. It increases the availability of active surface area for the ions from the electrolyte to interact with the carbon matrix \cite{younesi_analysis_2015}. This enhances the pseudocapacitance of the cell since most of the capacity comes from a surface-based charge storage mechanism. Pristine hemp fibers and Super-P observed peaks for both sp$^2$ bonded carbon atoms and carbon-oxygen bonds \cite{hussain_development_2019}. Hemp fibers are composed of proteins called lignin (Figure \ref{SF:lignin}), edestin and albumin which constitutes of arginine (Figure \ref{SF:arginine}) and glutamic acid (Figure \ref{SF:glutamicacid}).

Carbon 1s spectrum of Super-P consists of contribution from O–C–O and/or C=O bonds and a strong \ce{CH2}/\ce{CF2} bond. The material is produced from partial oxidation of petrochemical precursors exhibiting a large specific surface area and a very high electrical conductivity \cite{gnanamuthu_electrochemical_2011}. Carbon black consists of nearly spherical primary particles, which are fused together in form of aggregates. A perfect graphite surface containing only carbon atoms, without heteroatoms like oxygen and sulfur would give a very well-ordered structure. Therefore, presence of carbonyl groups created defects resulting in a less graphitic and more amorphous structure\cite{hao_carbonaceous_2013}. 
Carbon spectra for CFEx electrode was uniquely different with highly symmetrical peaks. The presence of $\pi$ electrons on fullerene's surface renders multiple $\pi$ satellite peaks. These peaks are characteristic signs of a \ce{C60} molecule \cite{skryleva_xps_2016}. The symmetrical peaks in the low energy range, 284–289 eV, have C 1s excitation to final states of $\pi$* character (in red), while the higher energy peaks appear due to C 1s excitation to final states of $\sigma$* character (in green) \cite{erbahar_spectromicroscopy_2016, poirier_carbon_1993}. %Existence of several peaks in the $\pi$ satellite of a C$_6_0$ molecule is caused by the angular quantisation of orbitals around the centre of the spherical molecule. 
%XPS analysis results... O 1s
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/XPSON}
    \caption{Oxygen 1s orbital XPS spectra of a) ACH, b) hemp fibers c) CFEx and d) Super-P cathodes. ACH and hemp fibers have significant amounts of aliphatic (red) and aromatic (pink) C=O groups present on the cathode surface; while Super-P and CFEx have low amount of oxygenated species at their surface. Nitrogen 1s orbital XPS spectrum of e) ACH, f) hemp fibers g) CFEx and h) Super-P cathodes. ACH displays distinct binding energies for pyridinic and pyrrolic N-species; hemp fibers show lower amount of surface proteins, while Super-P and CFEx have low concentrations of N-containing functional groups.}
  \label{figures:XPSON}
\end{figure}
Figure \ref{figures:XPSON}a-d represents the oxygen 1s peaks of ACH, hemp fibers, CFEx and Super-P cathodes. The peaks at $\approx$ 531 eV stands for an aliphatic -C=O bond. Aromatic C-OH bond has a higher binding energy at $\approx$ 533 eV. The presence of these carbonyl groups not only enhance the wettability of the electrodes, but also suggest towards a Faradaic process\cite{taberna_electrode_2006}. 
SPC and CFEx recorded less intense peaks due to negligible amounts C=O and C-O bonds present on their surface.
Looking at the nitrogen spectra in Figure 20, ACH has a distinct presence coming from keratin. Pyrrolic N species have a binding energy at 400.1 eV whereas pyridinic N-species appear at 398.3 eV. Guengen \textit{et al.} suggested that adding nitrogen molecules changed the electron distribution of carbon materials, enhances the wettability of the active material and  contributes to its capacitance \cite{gueguen_xps_2016}. Presence of strong N 1s peaks (Figure \ref{figures:XPSON}e) suggests enhanced wettability of the ACH cathode compared to others, which improves its charge-storage capacity. This might be another reason why ACH cathode recorded a higher specific capacity than other cathodes. 
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CV}
    \caption{Cyclic voltammograms of a) CFEx, b) ACH, c) Super-P and d) hemp fibers cathodes at a scan rate of 10 mV s$^-^1$ against \ce{Al3+}/Al as a counter/reference electrode in a two-electrode setup. ACH cathode observed a larger CV area than other cathodes, which comes from an additional pseudocapacitance, adding capacity to the system.}
  \label{figures:CV}
\end{figure}
Lastly, to confirm that ACH is surprisingly a psedocapacitive material, we compared cyclic voltammograms of all the cathodes at a scan rate of 10 mV/s. From Figure \ref{figures:CV}a-e, it was seen that ACH had a rectangular CV curve. Intercalation process is noticeable at a lower sweep rate (10 mV/s) with tiny redox peaks visible (Figure \ref{figures:CV}b). Redox pseudo-capacitance, which is usually observed at higher sweep rates (50 mV/s), can be seen in Figure \ref{SF:hair50mVs}. Since \ce{AlCl4-} anions electrochemically absorb onto the surface of ACH, the  need for long-range diffusion of ions through van der Waals gap decreases.

ACH proved to be the best carbon-based cathode among all the tested materials, with a specific capacity of 100 mAh g$^-{^1}$ at a potential of 1.9 V with a coulombic efficiency of ~90\%. Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers of ACH, hemp fibers and Super-P. 
We found that CFEx lacks a layered structure and it is mainly a cluster of \ce{C60} and \ce{C70} molecules. \ce{AlCl4-} anions seep in and out of the gaps in between the fullerenes changing its structure during insertion and expanding the crystal lattice (Figure \ref{figures:CFExmech}). Since the cathode maintains its structural integrity, coulombic efficiency remains stable throughout the cycles for CFEx cell. Hemp fibers and Super-P on the other hand, have a highly amorphous structure and degrades after every cycle, resulting in a low capacity value. Figure \ref{figures:CFExACHlong} compares the 50th cycle measurement for Al/ACH and Al/natural graphite cell. It not only displays a higher specific capacity than conventional graphite, but also a high battery voltage of 1.92 V with an energy density of 202 Wh kg$^-{^1}$.
 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CFExmech}
    \caption{Suggested mechanism for a \textbf{Al/CFEx} cell. AlCl$_4^_$ ions seeping in through the gaps present between fullerene molecules. A few AlCl$_4^_$ ions get absorbed on the cathode's surface resulting in a capacity purely from a non-Faradaic process.}
  \label{figures:CFExmech}
\end{figure}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CFExACHlong}
    \caption{Discharge capacities of a) ACH and b) CFEx cathodes at current rates of 50mAg$^-^1$, 500mAg$^-^1$, 1.0 Ag$^-^1$ and 1.5 Ag$^-^1$ along with their coulombic efficiencies. }
  \label{figures:CFExACHlong}
\end{figure}
\section{Experimental Section}
\subsection{Cathode preparation}
Slurry was prepared by mixing the active material (85$\%$ by wt.), 9$\%$ binder (PVDF, MTI Corp.) and 6$\%$ Super-P conductive carbon (99+$\%$ metals basis, Alfa Aesar) in N-methyl pyrrolidone NMP (anhydrous, 99.5$\%$, Sigma-Aldrich). For SPC slurry 94$\%$ active material and 6$\%$ binder was mixed together to form a slurry. It was ‘doctor-bladed’ on molybdenum foil used as a conductive substrate (thickness 0.1 mm, MTI Corp.) and dried in a vacuum oven at 120$^{\circ}$C for 12 hours to adhere the slurry on the substrate and evaporate the solvent. Specific loading of the materials ranged from 11-12 mg cm$^-{^2}$. 
\subsection{Electrolyte preparation}
Anhydrous AlCl$_3$ (Sigma-Aldrich) and EMImCl (97$\%$, Sigma-Aldrich) were mixed in a molar ratio of 1.3:1, at room temperature. EMImCl was baked in vacuum for 24 hours at 100°C to remove residual moisture. Small aliquots of AlCl$_3$ was added to EMImCl after every few minutes. The ionic liquid was stirred for 2-3 hours until a clear brown liquid was obtained. Since the electrolyte is hygroscopic in nature, it was prepared in a N$_2$-filled glove box with <0.1 ppm H$_2$O/O$_2$. 
\subsection{Cell assembly}
PEEK (polyether ether ketone) cells were used for electrochemical measurements (Figure \ref{SF:PEEK}). Molybdenum rods were used as current collectors. It was seen previously that steel rods reacted with the electrolyte forming a green-colored substance on the cathode. Slurry coated on molybdenum foil was used as the cathode and placed at bottom of the cell. Two glass microfibers (Grade GF/F, Whatman) were used as separators. 80$\mu$l of the electrolyte was used to wet the separator. Aluminium foil (thickness 0.1 mm, 99$\%$, GoodFellow) used as an anode and placed on top of the separator. It was assembled in a N$_2$-filled glove box. The cell was then sealed and wrapped with a paraffin film to avoid any air or moisture contact. Since this was a two-electrode setup, aluminium foil was used as both counter and reference electrode. The cell was taken out of the glove box and electrochemical measurements were performed.

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/GCDCall}
    \caption{Chronopotentiographs (Voltage vs. Time) curves of all tested cathodes.}
  \label{figures:GCDCall}
\end{figure}
\include{Supplementary}

\bibliographystyle{unsrt}  % Something must be wrong here....
\bibliography{zotero_refs}

\end{document}

### 2019-12-16 Supplementary.tex
Updates from Overleaf

\documentclass{article}
%\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[version=4]{mhchem}
% Include section in journal if known, otherwise delete
% \paperfield{Journal Section}
\title{Carbon cathodes for rechargeable aluminium-ion batteries}
%\corraddress{Author One PhD, Department, Institution, City, State or Province, Postal Code, Country}
%\presentadd[\authfn{2}]{Department, Institution, City, State or Province, Postal Code, Country}

% Include the name of the author that should appear in the running header
\begin{document}

\section*{Supporting Information}
\newcommand{\beginsupplement}{
               \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}
     }
\beginsupplement

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/ACHsyn}
    \caption{Synthesis of activated carbon from human hair using NaOH as the activating agent.}
  \label{SF:ACHsyn}
\end{figure}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/CFExsol}
    \caption{Synthesis of activated carbon from human hair using NaOH as the activating agent. The choice of temperature and activating agent plays a crucial role in determining pore size of the activated carbon.}
  \label{SF:CFExsol}
\end{figure}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=0.5\textwidth]{SF/keratin}
    \caption{Keratin: a protein abundantly found in human hair contains C-O, C=O, C-NH$_2$ bonds.} 
    \label{SF:keratin}
\end{figure}
%\begin{figure}[tbh!]
  %\centering
  %\includegraphics[width=0.5\textwidth]{SF/lignin}
    %\caption{Structure of Lignin- The lignin content of hemp will vary according to the part of the plant under observation. It contains a number of carbonyl, ester groups along with other proteins such as edestin and albumin.}
  %\label{SF:lignin}
%\end{figure}
%\begin{figure}[tbh!]
  %\centering
  %\includegraphics[width=0.5\textwidth]{SF/arginine}    \caption{Structure of Arginine- major component of hemp fibers containing C-N, C=O, C-O bonds.}
  %\label{SF:arginine}
%\end{figure}
%\begin{figure}[tbh!]
  %\centering
  %\includegraphics[width=0.5\textwidth]{SF/glutamicacid}
    %\caption{Structure of Glutamic acid- another protein found in hemp fibers containing C-O, C=O and C-N bonds.}
  %\label{SF:glutamicacid}
%\end{figure}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/XPSoverall}
    \caption{Overall spectra of ACH (blck), hemp fibers (blue), CFEx (green) and SUper-P(red).}
  \label{SF:XPSoverall}
\end{figure}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/hair50mVs}
    \caption{Cyclic voltammogram of ACH at a scan rate of 50 mV/s in a two electrode setup against \ce{Al3+}/Al showing a capacitor-like behaviour with no visible oxidation-reduction peaks unlike Figure \ref{figures:CV}b where we distinctly observed redox peaks.}
  \label{SF:hair50mVs}
\end{figure}
\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/PEEK}
    \caption{A custom-made two-electrode polyetherether ketone (PEEK) cell used for galvanostatic cycles and cyclic voltammetry.}
  \label{SF:PEEK}
\end{figure}
\end{document}

### 2019-12-16 manuscript.tex
Updates from Overleaf

@@
 \usepackage{setspace}
+\usepackage{tgtermes}
 \usepackage{subfig}
 \usepackage[version=4]{mhchem}
+\usepackage{threeparttable}
 \onehalfspacing
 \graphicspath{figures/}
-
+\usepackage{array, booktabs}
+\setlength{\arrayrulewidth}{0.5mm}
+\setlength{\tabcolsep}{8pt}
+\renewcommand{\arraystretch}{1.5}
 \title{Carbon cathodes for rechargeable aluminium-ion batteries}
-
 \author{
@@
 \begin{abstract}
- In this work, we compare four different forms of carbon: activated carbon from human hair (ACH), hemp fibers, a fullerene extract (CFEx) and Super-P carbon black as cathodes for non-aqueous aluminium-ion batteries.
+ In this work, we compare four different forms of carbon: activated carbon from human hair, activated carbon from hemp fibers, a fullerene mixture consisting of \ce{C60} and \ce{C70} fullerenes (CFEx) and Super-P carbon black (SPCB) as cathodes for non-aqueous aluminium-ion batteries.
 These materials differ in their general structure, porosity and morphology.
 The fullerenes display a crystalline structure, whereas hemp fibers, Super-P and ACH are amorphous in nature.
-Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^-{^1}$ with a coulombic efficiency of ~90\% at a current rate of 50 mV s$^-{^1}$.
-Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^-{^1}$ respectively.
-CFEx, a mixture of \ce{C60} (85\%) and \ce{C70} (15\%) fullerene, recorded its highest capacity at 78 mAh g$^-{^1}$ and maintained it for 50 cycles.
+Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$.
+Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively.
+CFEx recorded its highest capacity at 78 mAh g$^{-1}$ and maintained it for 50 cycles.
 The cells were charged and discharged to 2.45 V and 0.2 V respectively.
  \end{abstract}
+
 % keywords can be removed
 \keywords{carbon-based cathodes \and aluminium-ion battery \and ionic liquid \and human hair \and fullerene extract \and hemp fibers \and Super-P}
+
 \section{Introduction}
 Different varieties of carbon-based materials have been widely used in energy storage applications.
-Graphite, with its layered structure turned out to be an ideal intercalation cathode \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}.
-Activated carbon, owing to its porous structure, provided a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}.
-Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and aim to provide higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium.
-Exhaustive use of lithium and cobalt in LIBs would make portable batteries expensive in the coming years.
-One needs to switch to cost-effective alternatives.
-The above-mentioned properties make AIBs an interesting alternative\cite{ambroz_trends_2017-1}.
-We tested a number of rechargeable AIBs using an ionic liquid electrolyte with carbon-based cathodes.
+Graphite, with its layered structure turned out to be an ideal intercalation cathode material \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}.
+Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}.
+Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium.
+Thus, they offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}.
+In this work, we tested a number of rechargeable AIBs using an ionic liquid electrolyte with different carbon-based cathodes.
+The aim of this study was to systematically explore the properties of different carbon-materials when used as AIB cathodes.
+
 Graphite has been commonly used as a cathode in AIBs.
-It has a) a layered structure that enhances the intercalation process, b) good conductivity and c) a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V.
-Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, which showed specific capacities ranging from 60-250 mAh g$^-^1$.
+It has a layered structure that enhances the intercalation process, good conductivity, and a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V.
+Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$.
 The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge.
-X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism\cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}.
-Raman data showed that conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicated two stages of intercalation.
-XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively\cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
+X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}.
+Raman data showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation.
+XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
+
 \begin{figure}[tbh!]
@@
   \includegraphics[width=\textwidth]{SF/graphitemech}
-    \caption{Intercalation of AlCl$_4^_$ ions while cell charging and deintercalation during discharge in a \textbf{Al/graphite} cell.
-The interlayer distance between two graphite sheets is 3.3 $\AA$.}
+    \caption{Intercalation of \ce{AlCl4-} ions while cell charging and deintercalation during discharge in a Al/graphite cell. The interlayer distance between two graphite sheets is 3.3 \AA.}
   \label{SF:graphitemech}
 \end{figure}
+
 In this study, we compared four carbon-based materials with carbonised natural products.
-Super-P carbon has been used consistently as an additive to overcome any conductivity loss an active material suffers when a polymer binder such as PVDF, is added to it.
+Super-P carbon has been used consistently as an additive to overcome conductivity loss in the active electrode material (for example, when a polymer binder such as polyvinylidene fluoride (PVDF) is added to it).
 Using it as an active material, we tried to find if Super-P contributes any capacity of its own to the battery's specific capacity.
-Activated carbon from natural products like rice or wood have been previously used in super-capacitors\cite{hussain_development_2019, frackowiak_carbon_2001}.
-Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes .
+Activated carbon from natural products like rice or wood have been previously used in super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}.
+Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes.
 The pores absorb the charge carriers reversibly on their surface.
-Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes and got some interesting results.
+Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes.
+
 \section{Results and discussion}
+
 \begin{table}[tbh!]
-\caption{Comparing average battery metrics of all carbon cathodes} \label{table1}
-\begin{threeparttable}
+\caption{Comparing average battery metrics of carbon cathodes} \label{table1}
 \begin{center}
-\begin{tabular}{lcccc}
-\headrow
+\begin{tabular}{|lcccc|}
 \hline
-\thead{Active material} & \thead{\textbf{Size (pore size)}} & \thead\textbf{Specific capacity (mAh g$^-^1$)} & \thead\textbf{Cell efficiency (\%)} & \thead{\textbf{Cell voltage (V)}}\\
+Active material & {\textbf{Size}} & {\textbf{Specific capacity}} & {\textbf{Cell efficiency}} & {\textbf{Cell voltage}}\\
+ & {\textbf{(pore size)}} & {\textbf{(mAh g$^{-1}$)}} & {\textbf{(\%)}} & {\textbf{(V)}}\\
 \hline
-Activated carbon from human hair & 5\mu m & 102 & 97 & 1.9 \\
-Fullerene extract & 8.8\AA & 78 & 85 & 1.7 \\
-Hemp fibers & 2.3 \mu m & 49 & 75 & 1.8 \\
-Super-P & 300\AA & 46 & 40 & 1.5 \\
+Human hair & 5${\mu}$ m & 102 & 97 & 1.9 \\
+Fullerene mix & 8.8 \AA & 78 & 85 & 1.7 \\
+Hemp fibers & 2.3 $\mu$ m & 49 & 75 & 1.8 \\
+SPCB & 300 \AA & 46 & 40 & 1.5 \\
 \hline  % Please only put a hline at the end of the table
@@
 \end{center}
+\end{table}
 
-%\begin{tablenotes}
-%\item JKL, just keep laughing; MN, merry noise.
-%\end{tablenotes}
-\end{threeparttable}
-\end{table}
 \begin{figure}[tbh!]
@@
   \includegraphics[width=\textwidth]{figures/CDCall}
-    \caption{Specific capacities in the a) 1$^s^t$ and b) 50$^t^h$ cycle of ACH, hemp fibers, CFEx and Super-P cathodes at a current rate of 50 mA g$^-{^1}$.
-c) Cell efficiencies of cells at a current rate of 50 mAg$^-^1$.
-d) Specific capacities of carbon cells at current rates of 25 mAg$^-^1$, 50 mAg$^-^1$ and 100 mAg$^-^1$ in a two-electrode setup against \ce{Al^{3+}}/Al.
+    \caption{Specific capacities in the a) 1$^{st}$ and b) 50$^{th}$ cycle of human hair, hemp fiber, CFEx and SPCB cathodes at a current rate of 50 mA g$^{-1}$.
+c) Cell efficiencies of cells at a current rate of 50 mAg$^{-1}$.
+d) Specific capacities of carbon cells at current rates of 25 mAg$^{-1}$, 50 mAg$^{-1}$ and 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al.
 }
@@
 \end{figure}
-Our battery system comprised of a cathode, 99\% pure aluminium foil as an anode and a room temperature ionic liquid (RTIL) acting as the electrolyte.
-ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra showed presence of a few graphitic planes.
+
+Our battery system comprised a cathode, 99\% pure aluminium foil as an anode, and a room temperature ionic liquid (RTIL) acting as the electrolyte.
+ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra confirmed the presence of a few graphitic planes.
 Any number of graphite-like layers would allow \ce{AlCl4-} ions to intercalate when the cell was charged.
-However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had a crystalline lattice.
-Intercalation into the fullerene cage was not feasible because it needed a high amount of energy to break a C-C bond.
-We suggest that \ce{AlCl4-} anions seeped through the gaps present in between fullerenes without altering the molecular structure.
-Using a Neware BTS 3000 battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^-^1$ in Figure\ref{figures:CDCall}a and b.
-Structural changes in the cathode before and after cycles was studied using their Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.
-ACH cells recorded the highest capacity at 102-mAh g$^-{^1}$ and maintained it for 50 cycles.
-Coulombic efficiency was stable at ~95$\%$.
-Porous structure gave the material a high surface area that lead to an additional surface-based charge storage mechanism (observed in capacitors).Hemp fibers, due to their porous structure, observed a similar mechanism.
-Hemp cell showed a capacity of 56 mAh g$^-{^1}$ in its first cycle, which decreased to 45 mAh g$^-{^1}$ after 50 cycles.
-CFEx cell recorded its first discharge capacity at 79 mAh g$^-{^1}$, which shifted to just 78 mAh g$^-{^1}$. The cell maintained its coulombic efficiency at ~90$\%$. 
-Specific capacity of the Super-P cell decreased considerably after repeated charge/ discharge cycles.
-With an initial capacity of 84 mAh g$^-^1$, the value decreased to 47 mAh g$^-{^1}$ with a low coulombic efficiency of $\sim$40$\%$.
-A low coulombic efficiency, which was also observed in the hemp cell, can be attributed to degradation of cathode structure, also known as cathode pulverisation.
-It seems due to continuous cycling, weak bonds existing between sections of the cathode broke and agglomerated into smaller chunks of C atoms.
-As a result, the number of surface pores decreased, which reduced the cell's capacity (Figure \ref{figures:CDCall}c).
-Human hair has two components- cuticle and cortex.
-One way to make carbon porous is by treating it with an activating agent.
-Using activating agents especially alkali hydroxides improves the porosity and increases the surface area of material \cite{liu_hair-based_2017} .
-In this work, sodium hydroxide (NaOH) was used as the activating agent, which breaks the weak interactions existing between the overlapping cells in the cortex.
+However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had crystalline character.
+Intercalation of aluminium into the fullerene cages was not observed.
+We suggest that \ce{AlCl4-} anions migrated through the gaps present in between fullerenes without altering the molecular structure.
+Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{figures:CDCall}a and b).
+Structural changes in the cathode before and after the cycles were studied using Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.
+
+Figure \ref{figures:CDCall}a and b compares the specific capacities of all cells recorded in their 1$^{st}$ and 50${^th}$ cycles.
+Cells made of human hair displayed the highest capacity at around 100 mAh g$^{-1}$ with a coulombic efficiency at $\sim$95$\%$.
+High surface area due to the porous structure of the materials might have led to a additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}.
+Hemp cells displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles.
+CFEx cells displayed a capacity of around 80 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\%.
+With an initial capacity of 84 mAh g$^{-1}$, specific capacity of SPCB cells decreased to 47 mAh g$^{-1}$ and a low coulombic efficiency at around 40\% was recorded.
+Capacity for SPCB and hemp cells decreased considerably after repeated charge/discharge cycles.
+A low coulombic efficiency (observed in both hemp and SPCB cells) can be attributed to parasitic reactions of the battery.
+These can include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes}.
+However, capacity fade for CFEx and human hair cells was minimal.
+This suggest that CFEx and human hair have a more stable structure compared to hemp and SPCB and they store charge reversibly \cite{pramanick}.
+
+% In the above paragraph, you discuss 3 specific cells.
+This is suicidal (metaphorically speaking).
+In science you make a point by showing that something is reproducible.
+Having done just 3 expriments is asking for the reviewer to knock it down.
+You need to re-write this in a more general manner.
+
+The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonized precursor.
+Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas}.
+Using alkali hydroxides, such as sodium and potassium hydroxide at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}.
+In this work, sodium hydroxide (NaOH) was used as the activating agent.
 The reaction that takes place inside the matrix after adding NaOH is:
+
 \begin{center}
-    \\4NaOH + C \longrightarrow 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{qian_human_2013}
+    4NaOH + C $\longrightarrow$ 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{satish}
 \end{center}
 
-NaOH was reduced to Na, these atoms in turn expanded the carbon matrix.
-Oxidation of carbon formed \ce{CO2}, which created pores.
-An increase in temperature lead to Na activation, which was later removed from the matrix via channels created by \ce{CO2}.
-The channels created in this process provided path for \ce {AlCl4-} to intercalate inside the pores.
-The activating agent:carbon ratio and the calcinating temperature played an important role in determining the size of pores.
-The calcinating temperature used here was 750$^{\circ}$C.
-A schematic of ACH synthesis has been described in Figure \ref{SF:ACHsyn}.
-Dong \textit{et al.} suggested that at higher temperatures (>900$^{\circ}$C) pores start to collapse resulting in graphitic sheets \cite{dong_commercial_2019}.
-Fibers obtained from Hemp (\textit{Cannabis Sativa L.}) have been used in several commercial items including paper, textiles, clothing, biodegradable plastics, paints, and bio-fuels.
-They have been used as reinforcements in composite materials and are capable of replacing glass fibers.
-Hemp fibers have a high moisture content which can be removed after high temperature treatment\cite{hussain_development_2019}.
-For creating activated carbon from these fibers, potassium hydroxide (KOH) was used as the activating agent.
-Since the samples were obtained from Carbon Valley\textsuperscript{\textregistered}, we are unable to report the precise calcinating temperature used.
-Unfortunately the structural domains appeared to have been damaged after this process.
-This phenomena negatively impacted its charge-storing capacity.
-Fullerenes have a fused-ring structure.
-The nucleus-to-nucleus diameter is 7.1\AA\ and van der Waals diameter is 11\AA\ in a single crystal.
-Presence of $\pi$-electrons on its surface makes it a good electron acceptor.
-However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity\cite{loutfy_fullerene_2002, winkler_two-component_2007}.
-Electrochemical reduction of \ce{C60} to \ce{C60^{-3}} is highly reversible suggesting they are capable of giving reversible capacities.
-However, they are weak battery cathode materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}.
-To test their solubility in \ce{AlCl3}-EMImCl ionic liquid, 100 mg of CFEx was mixed in the electrolyte and stirred for 4 hours.
-For comparison, we mixed hemp fibers in another vial.
-The vials were left to stand for 24 hours in a \ce{N2}-filled glove box.
-A phase separation was observed with hemp fibers but not for CFEx indicating it dissolved in the electrolyte (Figure \ref{SF:CFExsol}.
-It has been reported in Li-S batteries that poly-sulphides produced during charge-discharge were soluble in the electrolyte.
-It forms an insulating layer of \ce{Li2S} on the anode, which resulted in capacity fading \cite{sun_effect_2017, yan_2d_nodate}.
-However, reversible capacities obtained after 50 cycles suggested no such molecules were formed with \ce{AlCl3}/EmImCl electrolyte.
+NaOH was reduced to free metal, Na, these atoms in turn expanded the carbon matrix after intercalating into the carbon structure.
+Increased temperature ($\sim$900$^{\circ}$ C) forces the  atoms out of the carbon matrix, thus creating micropores.
+Oxidation of carbon from oxygen atoms of the hydroxide group forms \ce{CO2} providing routes for channeling the Na atoms into the internal structure leading to well-connected porous structure \cite{satish}.
+The calcinating temperature used here was 750$^{\circ}$ C.
+Figure \ref{SF:ACHsyn} displays the flowchart for activated carbon synthesis.
+
+% Paragraph above: you need to prove/reason every statement that you make. You just claim a lot of stuff without providing any evidence. Also: ARTICLES!!!!!
+
+%Unfortunately the structural domains appeared to have been damaged after this process. This phenomena negatively impacted its charge-storing capacity.
+
+% Above paragraph: Lots of unnecerssary information (see comments).
+Focus on what is relevant.
+Also sentences like the Carbon Valley one are suicidal.
+When you write, always have your worst scientific enemy in mind and write it so that you win.
+
+Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals diameter of 11 \AA in a single crystal.
+However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}.
+They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}.
+To test their solubility in \ce{AlCl3}-EMImCl, 100 mg of CFEx was mixed in the electrolyte and stirred for 24 hours.
+The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box.
+CFEx seemed to dissolve in our electrolyte (Figure \ref{SF:CFExsol} since no phase separation was observed.
+It has been reported that poly-sulphides formed during cycling in a lithium-sulfur battery, are soluble in the electrolyte.
+They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}.
+Since no such effect was observed in aluminium-fullerene cells, this phenomena does not seem to impact the charge-storing capacity of CFEx.
+On the contrary, the cells displayed excellent capacity retention at various current rates(Figure \ref{figures:CDCall}d).
+
  \begin{figure}[tbh!]
@@
 Super-P has a very amorphous structure with a few graphite-like planes present in it.
-AlCl$_4^_$ ions intercalate into those layers and give the cell its capacity.
+\ce{AlCl4-} ions intercalate into those layers and give the cell its capacity.
 However, cathode pulverisation results in capacity fading.}
@@
 \end{figure}
-Pore size for Super-P ranges from ~30-50 nm \cite{younesi_analysis_2015}.
-It has the least graphitic structure when compared to ACH and hemp fibers.
-Loosely held structures, which disintegrated rapidly after every cycle resulted in reduced capacity and low coulombic efficiency values.
+
+Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure.
+Its pore size ranges from $\sim$30-50 nm \cite{younesi_analysis_2015}.
+SPCB has the least graphitic structure if compared to human hair and hemp fibers.
+It seems continuous cycling might have destroyed the arrangement of the carbon atoms, which resulted in poor capacity retention and low coulombic efficiencies.
 
@@
     \caption{Suggested mechanism for a \textbf{Al/hemp} cell.
-The fibers have a large pore size (2.0-2.5 \mu m) which allow the AlCl$_4^_$ to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
+The fibers have a large pore size (2.0-2.5 $\mu$m) which allow the \ce{AlCl4-} to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
   \label{figures:hempmech}
 \end{figure}
+
  \begin{figure}[tbh!]
@@
 \end{figure}
-Since it has been previously established that intercalation of \ce{AlCl4-} takes place in carbon materials during cell charge, we focused our analysis on the charged electrodes.
-Figure \ref{figures:raman} illustrates Raman spectra of the tested cathodes.
-Pristine ACH, hemp fibers and Super-P had a significant D-band indicating a distorted lattice.
-Increased intensity of D band can be seen in charged electrodes at ~1300 cm$^-{^1}$ (ACH), 1329.7 cm$^-{^1}$ (hemp fibers), and 1352.0 cm$^-{^1}$ (Super-P) indicating an increase in the lattice defects and deformities.
-Hemp fibers and ACH observed an increased FWHM (full width at half maximum) of both D and G bands indicating a loss in symmetry.
-Intercalation of ions or surface adsorption of anions onto the porous carbon cathode, would alter the ordered structure on the surface.
-We suggest capacitive intercalation mechanism as well as a redox pseudocapacitance where \ce{AlCl4-} ions electrochemically adsorb onto the surface \cite{brezesinski_ordered_2010}.
-The main feature in a fullerene Raman spectrum was a sharp line observed at 1460 cm$^-^1$, which is known as the 'pentagonal pinch mode'.
-\ce{C60} is composed of \ce{sp2} bonded carbon atoms.
-Sharpness of the band indicates a uniform nature of the bonds.
-However, the spectrum of C$_7_0$ has multiple bands.
-Reduction in its molecular symmetry increases the number of active Raman bands \cite{kimbrell_analysis_2014}.
-Pristine CFEx electrode observed characteristic peaks of both \ce{C60} and \ce{C70} at 1459.3 cm$^-{^1}$ and 1564 cm$^-{^1}$ respectively in Figure \ref{figures:raman}c.
-An interesting observation was that pristine and charged CFEx electrodes had a similar-looking spectra after cycling.
-Since Raman spectroscopy is sensitive to very minute differences in molecular morphology, the results suggested that the structure remained intact.
-Another interesting observation was made in charged ACH electrode (Figure \ref{figures:raman}a).
-A new peak appeared at 1466 cm$^-{^1}$.
-A similar band splitting was observed by Wang \textit{et al} \cite{wang_kish_2017} while charging natural graphite and AlCl$_4^-$ ions intercalated into the cathode layers.
-This peak appeared due to vibration of carbon atoms in a plane adjacent to intercalant layer planes.
-We observed no such effect was observed for any other cathode.
-Since the Al/ACH cell maintained a highly reversible capacity of 102 mAhg$^-^1$ after 50 cycles, we assume ACH underwent a similar mechanism, where \ce{AlCl4-} ions intercalate into the cathode during charge.
-ACH has a high surface area and an inter-connected mesoporosity.
-The layered domains present in it enable insertion of \ce{AlCl4-}, while a few anions get electrochemically adsorbed onto the surface through a charge-transfer process resulting in a redox pseudo-capacitance.
-All these processes seem to take place at the same time without changing the reaction kinetics.
-Additionally, presence of both an amorphous and crystalline structure in this material increases the charge-storage capacity of the material \cite{brezesinski_ordered_2010}.
-This might be the reason why ACH shows a remarkable reversibility.
-Schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}.
-Hemp fibers and Super-P had lattice deformities to begin with, which were enhanced after the cell underwent the preliminary galvanostatic cycles.
-This decreased capacity after every cycle.
+
+In aluminum-graphite cells, it has been established that \ce{AlCl4-} ions intercalate while charging \cite{lin_ultrafast_2015}.
+Since the materials we tested have graphitic planes present, we focused our analysis on the pristine and charged electrodes.
+Figure \ref{figures:raman} displays Raman spectra of the tested cathodes.
+Pristine human hair, hemp fibers and SPCB had a significant D-band present indicating absence of an ordered structure with presence of lattice defects and deformities (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB).
+Figure \ref{figures:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules.
+The 'pentagonal pinch mode', which is usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$.
+However, \ce{C70} has multiple bands.
+Reduction in its molecular symmetry increases the number of vibrational modes, thus increasing the active Raman bands \cite{kimbrell_analysis_2014}.
+Pristine CFEx cathode was composed of both \ce{C60} and \ce{C70} Raman bands as seen in Figure \ref{figures:raman}c.
+It was interesting to note that charged CFEx cathodes looked strikingly similar.
+Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the structure remained intact after cycles.
+Human hair has a high surface area and an inter-connected mesoporosity.
+The charged cathodes showed a higher FWHM which suggests an increase in the lattice defects.
+Obviously, these defects arise after intercalation of chloroaluminates; it is assumed that these ions intercalate into the few graphitic planes present in the carbon matrix.
+In addition, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}.
+Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge\cite{brezesinski_ordered_2010}.
+A schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}.
+%contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.  
+Hemp fibers and SPCB had fewer graphitic planes and a highly disordered structure to begin with.
+The lattice defects seemed to increase after galvanostatic cycles.
+Continuous intercalation or absorption of ions on their surface would have further destroyed the cathode structure.
+This might be the reason why hemp and SPCB cells failed to retain capacity after a few cycles.
+However, CFEx does not have graphitic planes.
+It consists of a bunch of \ce{C60} and \ce{C70} fullerenes.
+Insertion of \ce{AlCl4-} ions inside the cage-like structure would be thermodynamically impossible.
+Since the fullerenes have a very high surface area, surface adsorption of ions is likely \cite{adams}.
+Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes \ref{figures:CFExmech}.
+Capacity retention of the aluminium-CFEx cells suggests that the interaction between the fullerenes and \ce{AlCl4-} ions takes place in a systematic way.
+
 \begin{figure}[tbh!]
@@
 \end{figure}
-Above results seem to be in good agreement with SEM images in Figure 9, where we compared pristine (Figure \ref{figures:SEM}a, b, c and d) and charged electrodes (\ref{figures:SEM}e,f,g and h).
-ACH and hemp fibres have a porous structure (Figure \ref{figures:SEM}a and 9b), which looked visibly degraded after cycles (Figure \ref{figures:SEM}e and f).
-Agglomeration of carbon atoms increases the edge defects in a material.
-This explains the high intensity of D-bands of these cathodes, Figure \ref{figures:raman}.
-Surface morphology of CFEx (Figure \ref{figures:SEM}c did not change a lot after charge (Figure \ref{figures:SEM}g), similar to our observations in its Raman spectra.
+
+In Figure \ref{figures:SEM}, we compared the SEM images of pristine (Figure \ref{figures:SEM}a, b, c and d) and charged (\ref{figures:SEM}e,f,g and h) cathodes of all tested materials.
+Hemp and SPCB had a porous structure (Figure \ref{figures:SEM}b and d) to begin with, which degraded after a few cycles (Figure \ref{figures:SEM}f and h).
+Significant agglomeration occurred in hemp and SPCB cathodes after continuous cycling.
+
 \begin{figure}[tbh!]
@@
   \includegraphics[width=\textwidth]{figures/XRD}
-    \caption{XRD spectra comparing a pristine (black), charged (green) and discharged (red) a) CFEx and b)ACH cathode to study changes in their lattice after 50 galvanostatic cycles in a two-electrode setup against \ce{Al3+}/Al with characteristic peaks marked for \ce{C60} (in grey) and \ce{C70} (in blue).}
+    \caption{XRD spectra comparing a pristine (black), charged (green) and discharged (red) a) CFEx and b)ACH cathode to study changes in their lattice after 50 galvanostatic cycles in a two-electrode setup against \ce{Al$^{3+}$/Al} with characteristic peaks marked for \ce{C60} (in grey) and \ce{C70} (in blue).}
   \label{figures:XRD}
 \end{figure}
-To confirm the reversible electrochemical processes taking place in CFEx and ACH, we examined their XRD spectra (pristine, charged and discharged) in Figure \ref{figures:XRD}a and b respectively.
-Pristine cathode recorded the characteristic peaks of both \ce{C60} and \ce{C70}, which reappeared after discharge suggesting a reversible process.
-However, charged electrode observed new diffraction peaks which can be attributed to lattice deformities taking place at the electrode/electrolyte interface.
-We calculated the unit cell lattice parameters for both pristine and charged cathode for a \ce{C60} molecule.
+
+To fully understand the mechanism in CFEx and human hair, we examined their XRD spectra in Figure \ref{figures:XRD}.
+Pristine, charged and discharged cathodes of CFEx and human hair were compared in Figure \ref{figures:XRD}a and b respectively.
+Pristine cathodes displayed the characteristic peaks of both \ce{C60} and \ce{C70} at 2$\theta$ values of 10.9$^{\circ}$, 17.8$^{\circ}$, 20.9$^{\circ}$ and 28.2$^{\circ}$ for \ce{C60} and 18.9$^{\circ}$, 19.3$^{\circ}$ and 21.8$^{\circ}$ for \ce{C70} molecules.
+Charged electrodes displayed new diffraction peaks at lower 2$\theta$ values.
+However, after discharge, the XRD pattern resembled the pristine cathode.
+This data strongly suggests a reversible process.
+To confirm, we calculated the unit cell lattice parameters for both pristine and charged cathodes for a \ce{C60} molecule.
 The unit cell had a tetragonal crystal system with space group of P42/mmc and a space group number 131 (ICDD: 04-013-1339 for \ce{C60}).
-Lattice parameter 'a' and 'b' for the charged electrode changed from 9.06\AA to 9.57\AA .
-Lattice parameter 'c' changed from 15.03\AA to 15.65\AA, in Figure \ref{figures:CFExcryst}a and b.
+Lattice parameter 'a' and 'b' for the charged electrode changed from 9.06 \AA to 9.57 \AA .
+Lattice parameter 'c' changed from 15.03 \AA to 15.65 \AA, in Figure \ref{figures:CFExcryst}a and b.
 Lattice parameters for discharged cathode were closer to pristine values.
-The changes in the fullerene structure suggested a reversible intercalation process taking place, where the unit cells shifted from their original location during charge and returned back after discharge.
+These changes suggested a reversible intercalation process taking place.
 A possible site for \ce{AlCl4-} intercalation is depicted in Figure \ref{figures:CFExcryst}c.
-XRD spectra for ACH electrodes was inconclusive (Figure \ref{figures:XRD}b).
-Pristine cathode observed very broad peaks suggesting the extreme amorphous nature of the material.
-However, the material seemed to have a more ordered structure after the galvanostatic cycles.
-It seems that surface-based charge-storage was more dominant than the intercalation process.
-This is why presence of crystallinity in the active material does not limit the surface-based charge storage and therefore, the capacity remains same \cite{kim_synthesis_2006, jow_factors_2018}.
+XRD spectra for human hair cathodes was inconclusive (Figure \ref{figures:XRD}b).
+Pristine cathode showed broad peaks suggesting an amorphous and highly porous structure.
+However, the material became more ordered after cycles.
+Charged and discharged cathodes have similar patterns which means no structural changes took place in aluminium-hair batteries.
+Also, presence of crystallinity in an active material does not limit the surface-based charge storage \cite{kim_synthesis_2006, jow_factors_2018}.
+So, we hypothesise that human hair followed a capacitor-like behaviour after intercalation of ions in the initial cycles.
+
  \begin{figure}[tbh!]
@@
   \includegraphics[width=\textwidth]{figures/ACHmech}
-    \caption{Suggested mechanism for a \textbf{Al/ACH} cell.
-ACH has a porous structure which allows AlCl$_4^_$ ions to get absorbed as well as reversibly intercalate into the graphitic planes, giving additional capacity to the cell.}
+    \caption{Suggested mechanism for an aluminium-human hair cell.}
   \label{figures:ACHmech}
@@
 \end{figure}
+
 %Charged Super-P and hemp fiber electrodes underwent degradation and appeared clumped together resulting in capacity decay.
 This was visible from their electrochemical results where a rapid decrease in capacity and cell efficiency was noted.
+
 %XPS analysis results... C 1s 
@@
 \end{figure}
-We performed X-ray photoelectron spectroscopy on our cathodes to understand the kinds of reactions the cathodes could take part in.
-We observed ACH, hemp fibers and Super-P had similar looking peaks for carbon 1s orbital, Figure \ref{figures:XPSC}.
-Peaks for sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds (formed between PVDF and the active material) appeared for ACH, hemp fibers and Super-P cathodes.
-To understand the presence of these bonds,we looked into the composition of these active materials.
-Hair is mainly composed of a protein called keratin displayed in Figure \ref{SF:keratin}.
-Keratin constitutes of various C-H, C=O, C-OH and C-NH$_2$ bonds with their respective binding energies as observed in Figure \ref{figures:XPSC}a.
-Sulphur is an essential part of this protein, a C-S bond can be observed at 286.94 eV (blue peak).
+
+We observed XPS spectra of all pristine cathodes to understand their composition.
+Human hair, hemp fibers and SPCB had similar looking peaks for carbon 1s orbital as shown in figure \ref{figures:XPSC}.
+Binding energies suggesting sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds (formed between the binder and active material) appeared in hair, hemp fibers and SPCB cathode spectra.
+Hair is mainly composed of a protein called keratin displayed in Figure \ref{SF:keratin} and the multiple chemical environments of carbon in Figure \ref{figures:XPSC}a) are derived from Keratin.
+Sulphide bonds are an essential part of this protein and a C-S binding energy is observed at 286.94 eV (blue peak).
+
 \begin{table}
-\caption{XPS data sheet for the tested cathodes with \textbf{Carbon 1s} peaks pointing C-H/ C-C, C-O/ C-OH, C=O/ O-C=O and C-F bonds, \textbf{Nitrogen 1s} peaks for pyrrolic and pyridnic N nods and \textbf{Oxygen 1s} peaks for aliphatic C-O and aromatic C=O peaks.} \label{table2}
-\begin{tabular}{cccccccc}
+\caption{Carbon 1s peaks for various binding energies.} \label{table2}
+\begin{tabular}{|cccccccc|}
 \hline
-\thead {Active} & \thead{C-H/} & \thead{C-O/} & \thead{C=O/} & \thead{C-F} & \thead{Pyrrolic N/} & \thead{aliphatic C-O} & \thead{aromatic C=O}\\
-\thead {material} & \thead{C-C} & \thead{C-OH} & \thead{O-C=O} & \thead{} & \thead{Pyridinic N} & \thead{} & \thead{}\\
-\hline\\
-ACH & 284.5 eV & 285.8 eV & 288.4 eV & 290.2 eV & 400.2 eV/ & 533.0 eV & 531.2 eV\\
+Active & C-H/ & C-O/ & C=O/ & C-F & Pyrrolic N/ & aliphatic C-O & aromatic C=O\\
+material & C-C & C-OH & O-C=O & & Pyridinic N & & \\
+\hline
+Human hair & 284.5 eV & 285.8 eV & 288.4 eV & 290.2 eV & 400.2 eV/ & 533.0 eV & 531.2 eV\\
 & & & & & 398.3 eV & & \\
@@
 Hemp fibers & 284.5 eV & 286.0 eV & 288.7 eV & 290.5 eV & 400.3 eV & 532.9 eV & 531.4 eV\\
-Super-P & 284.3 eV & 286.7 eV & 288.0 eV & 290.7 eV & 400.2 eV & 532.8 eV & ---\\
+SPCB & 284.3 eV & 286.7 eV & 288.0 eV & 290.7 eV & 400.2 eV & 532.8 eV & ---\\
 \hline
@@
 \end{table}
-The oxygen-containing carbonyl and ester groups improve the wettability of cathode materials.
-It increases the availability of active surface area for the ions from the electrolyte to interact with the carbon matrix \cite{younesi_analysis_2015}.
-This enhances the pseudocapacitance of the cell since most of the capacity comes from a surface-based charge storage mechanism.
-Pristine hemp fibers and Super-P observed peaks for both sp$^2$ bonded carbon atoms and carbon-oxygen bonds \cite{hussain_development_2019}.
-Hemp fibers are composed of proteins called lignin (Figure \ref{SF:lignin}), edestin and albumin which constitutes of arginine (Figure \ref{SF:arginine}) and glutamic acid (Figure \ref{SF:glutamicacid}).
 
-Carbon 1s spectrum of Super-P consists of contribution from O–C–O and/or C=O bonds and a strong \ce{CH2}/\ce{CF2} bond.
-The material is produced from partial oxidation of petrochemical precursors exhibiting a large specific surface area and a very high electrical conductivity \cite{gnanamuthu_electrochemical_2011}.
-Carbon black consists of nearly spherical primary particles, which are fused together in form of aggregates.
+Functional groups that contain oxygen, such as carbonyl and ester groups, improve the wettability of a material and increases the availability of active surface area \cite{younesi_analysis_2015}.
+SPCB is produced from partial oxidation of petrochemical precursors and exhibits a large specific surface area with a very high electrical conductivity \cite{gnanamuthu_electrochemical_2011}.
 A perfect graphite surface containing only carbon atoms, without heteroatoms like oxygen and sulfur would give a very well-ordered structure.
-Therefore, presence of carbonyl groups created defects resulting in a less graphitic and more amorphous structure\cite{hao_carbonaceous_2013}.
-Carbon spectra for CFEx electrode was uniquely different with highly symmetrical peaks.
-The presence of $\pi$ electrons on fullerene's surface renders multiple $\pi$ satellite peaks.
+Presence of impurities such as carbonyl groups creats defects resulting in a less graphitic and more amorphous structure\cite{hao_carbonaceous_2013}.
+XPS spectra for CFEx electrodes was uniquely different with highly symmetrical peaks.
+The presence of $\pi$ electrons on the fullerene's surface results in  multiple $\pi$ satellite peaks.
 These peaks are characteristic signs of a \ce{C60} molecule \cite{skryleva_xps_2016}.
-The symmetrical peaks in the low energy range, 284–289 eV, have C 1s excitation to final states of $\pi$* character (in red), while the higher energy peaks appear due to C 1s excitation to final states of $\sigma$* character (in green) \cite{erbahar_spectromicroscopy_2016, poirier_carbon_1993}.
+The symmetrical peaks appear in both high (in green) and low energy ranges (in red, 284–289 eV)\cite{erbahar_spectromicroscopy_2016, poirier_carbon_1993}.
 %Existence of several peaks in the $\pi$ satellite of a C$_6_0$ molecule is caused by the angular quantisation of orbitals around the centre of the spherical molecule. 
 %XPS analysis results... O 1s
+
 \begin{figure}[tbh!]
   \centering
-  \includegraphics[width=\textwidth]{figures/XPSON}
-    \caption{Oxygen 1s orbital XPS spectra of a) ACH, b) hemp fibers c) CFEx and d) Super-P cathodes.
-ACH and hemp fibers have significant amounts of aliphatic (red) and aromatic (pink) C=O groups present on the cathode surface; while Super-P and CFEx have low amount of oxygenated species at their surface.
-Nitrogen 1s orbital XPS spectrum of e) ACH, f) hemp fibers g) CFEx and h) Super-P cathodes.
-ACH displays distinct binding energies for pyridinic and pyrrolic N-species; hemp fibers show lower amount of surface proteins, while Super-P and CFEx have low concentrations of N-containing functional groups.}
+  \includegraphics[width=0.8\textwidth]{figures/XPSON}
+    \caption{XPS spectra of O 1s orbital for a) human hair, b) hemp fibers c) CFEx and d) SPCB cathodes.
+Hair and hemp fibers contained significant amounts of aliphatic (red) and aromatic (pink) C=O groups  compared to CFEx and SPCB.
+Binding energies for N 1s orbital of e) hair, f) hemp fibers g) CFEx and h) SPCB cathodes.
+Human hair displayed distinct binding energies for pyridinic and pyrrolic N-species; hemp fibers, CFEx and SPCB had smaller amounts of surface proteins.}
   \label{figures:XPSON}
 \end{figure}
-Figure \ref{figures:XPSON}a-d represents the oxygen 1s peaks of ACH, hemp fibers, CFEx and Super-P cathodes.
-The peaks at $\approx$ 531 eV stands for an aliphatic -C=O bond.
-Aromatic C-OH bond has a higher binding energy at $\approx$ 533 eV.
-The presence of these carbonyl groups not only enhance the wettability of the electrodes, but also suggest towards a Faradaic process\cite{taberna_electrode_2006}.
-SPC and CFEx recorded less intense peaks due to negligible amounts C=O and C-O bonds present on their surface.
-Looking at the nitrogen spectra in Figure 20, ACH has a distinct presence coming from keratin.
-Pyrrolic N species have a binding energy at 400.1 eV whereas pyridinic N-species appear at 398.3 eV.
-Guengen \textit{et al.} suggested that adding nitrogen molecules changed the electron distribution of carbon materials, enhances the wettability of the active material and  contributes to its capacitance \cite{gueguen_xps_2016}.
-Presence of strong N 1s peaks (Figure \ref{figures:XPSON}e) suggests enhanced wettability of the ACH cathode compared to others, which improves its charge-storage capacity.
-This might be another reason why ACH cathode recorded a higher specific capacity than other cathodes.
+
+Figure \ref{figures:XPSON}a-d shows various binding energies for O 1s orbital.
+As mentioned earlier, oxygen-containing functional groups enhance the wettability of a material and presence of oxygen atoms make redox reactions feasible \cite{li_effect_2011, oh_oxygen}.
+Oxygen-containing surface functional groups can provide pseudo-capacitance by reacting with electrolyte ions \cite{bleda_martinez}.
+This might be one of the reasons why aluminium-hair and aluminium-fullerene batteries performed better than others.
+
  \begin{figure}[tbh!]
@@
   \includegraphics[width=\textwidth]{figures/CV}
-    \caption{Cyclic voltammograms of a) CFEx, b) ACH, c) Super-P and d) hemp fibers cathodes at a scan rate of 10 mV s$^-^1$ against \ce{Al3+}/Al as a counter/reference electrode in a two-electrode setup.
+    \caption{Cyclic voltammograms of a) CFEx, b) ACH, c) Super-P and d) hemp fibers cathodes at a scan rate of 10 mV s$^{-1}$ against \ce{Al3+}/Al as a counter/reference electrode in a two-electrode setup.
 ACH cathode observed a larger CV area than other cathodes, which comes from an additional pseudocapacitance, adding capacity to the system.}
@@
 \end{figure}
-Lastly, to confirm that ACH is surprisingly a psedocapacitive material, we compared cyclic voltammograms of all the cathodes at a scan rate of 10 mV/s.
-From Figure \ref{figures:CV}a-e, it was seen that ACH had a rectangular CV curve.
-Intercalation process is noticeable at a lower sweep rate (10 mV/s) with tiny redox peaks visible (Figure \ref{figures:CV}b).
-Redox pseudo-capacitance, which is usually observed at higher sweep rates (50 mV/s), can be seen in Figure \ref{SF:hair50mVs}.
-Since \ce{AlCl4-} anions electrochemically absorb onto the surface of ACH, the  need for long-range diffusion of ions through van der Waals gap decreases.
 
-ACH proved to be the best carbon-based cathode among all the tested materials, with a specific capacity of 100 mAh g$^-{^1}$ at a potential of 1.9 V with a coulombic efficiency of ~90\%.
-Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers of ACH, hemp fibers and Super-P.
-We found that CFEx lacks a layered structure and it is mainly a cluster of \ce{C60} and \ce{C70} molecules.
-\ce{AlCl4-} anions seep in and out of the gaps in between the fullerenes changing its structure during insertion and expanding the crystal lattice (Figure \ref{figures:CFExmech}).
-Since the cathode maintains its structural integrity, coulombic efficiency remains stable throughout the cycles for CFEx cell.
-Hemp fibers and Super-P on the other hand, have a highly amorphous structure and degrades after every cycle, resulting in a low capacity value.
-Figure \ref{figures:CFExACHlong} compares the 50th cycle measurement for Al/ACH and Al/natural graphite cell.
-It not only displays a higher specific capacity than conventional graphite, but also a high battery voltage of 1.92 V with an energy density of 202 Wh kg$^-{^1}$.
+Lastly, to confirm that ACH is a psedocapacitive material, we compared cyclic voltammograms of all cathodes at a scan rate of 10 mV s$^{-1}$.
+From Figure \ref{figures:CV}a-e, it was seen that human hair had a rectangular capacitor-like CV curve.
+However, redox processes were noticeable at a lower scan rate (10 mV s$^{-1}$) and tiny redox peaks visible (Figure \ref{figures:CV}b).
+At a higher scan rate (50 mV s$^{-1}$), the redox peaks disappeared and the material displays solely a capacitor-like behaviour, shown in Figure \ref{SF:hair50mVs} \cite{guan_capacitive, dupont_separating}.
+
  \begin{figure}[tbh!]
@@
     \caption{Suggested mechanism for a \textbf{Al/CFEx} cell.
-AlCl$_4^_$ ions seeping in through the gaps present between fullerene molecules.
-A few AlCl$_4^_$ ions get absorbed on the cathode's surface resulting in a capacity purely from a non-Faradaic process.}
+\ce{AlCl4-} ions seeping in through the gaps present between fullerene molecules.
+A few \ce{AlCl4-} ions get absorbed on the cathode's surface resulting in a capacity purely from a non-Faradaic process.}
   \label{figures:CFExmech}
 \end{figure}
+
 \begin{figure}[tbh!]
@@
   \includegraphics[width=\textwidth]{figures/CFExACHlong}
-    \caption{Discharge capacities of a) ACH and b) CFEx cathodes at current rates of 50mAg$^-^1$, 500mAg$^-^1$, 1.0 Ag$^-^1$ and 1.5 Ag$^-^1$ along with their coulombic efficiencies. }
+    \caption{Discharge capacities of a) ACH and b) CFEx cathodes at current rates of 50mAg$^{-1}$, 500mAg$^{-1}$, 1.0 Ag$^{-1}$ and 1.5 Ag$^{-1}$ along with their coulombic efficiencies. }
   \label{figures:CFExACHlong}
 \end{figure}
+
+% Are the following the conclusions?
+\section{Conclusion}
+ACH proved to be the best carbon-based cathode among all the tested materials, with a specific capacity of 100 mAh g$^{-1}$ at a potential of 1.9 V with a coulombic efficiency of $\sim$90$\%$.
+Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers of ACH, hemp fibers and Super-P.
+We found that CFEx lacks a layered structure and it is mainly a cluster of \ce{C60} and \ce{C70} molecules.
+\ce{AlCl4-} anions seep in and out of the gaps in between the fullerenes changing its structure during insertion and expanding the crystal lattice (Figure \ref{figures:CFExmech}).
+Since the cathode maintains its structural integrity, the coulombic efficiency remains stable throughout the cycles for CFEx cell.
+Hemp fibers and Super-P on the other hand, have a highly amorphous structure and degrades after every cycle, resulting in a low capacity value.
+Figure \ref{figures:CFExACHlong} compares the 50th cycle measurement for Al/ACH and Al/natural graphite cell.
+It not only displays a higher specific capacity than conventional graphite, but also a high battery voltage of 1.92 V with an energy density of 202 Wh kg$^{-1}$.
+
 \section{Experimental Section}
+\subsection{Chemicals}
+\subsubsection*{Activated carbon from human hair}
+\subsubsection*{Activated carbon from hemp fibers}
+The material was provided by Carbon Valley and used as received.
+\subsubsection*{Fullerene extract}
+C60/C70, approx. 85\% C60, 14\% C70, and 1\% higher fullerenes, was purchased from SES research and used as received.
+\subsubsection*{Super-P carbon black}
+Super-P conductive carbon, 99+\% metals basis was purchased from Alfa-Aesar and used as received
+
 \subsection{Cathode preparation}
-Slurry was prepared by mixing the active material (85$\%$ by wt.), 9$\%$ binder (PVDF, MTI Corp.) and 6$\%$ Super-P conductive carbon (99+$\%$ metals basis, Alfa Aesar) in N-methyl pyrrolidone NMP (anhydrous, 99.5$\%$, Sigma-Aldrich).
-For SPC slurry 94$\%$ active material and 6$\%$ binder was mixed together to form a slurry.
+A slurry was prepared by mixing the active material (85$\%$ by wt.), 9$\%$ binder (PVDF, MTI Corp.) and 6$\%$ Super-P conductive carbon (99+$\%$ metals basis, Alfa Aesar) in N-methyl pyrrolidone NMP (anhydrous, 99.5$\%$, Sigma-Aldrich).
+For SPCB slurry 94$\%$ active material and 6$\%$ binder was mixed together to form a slurry.
 It was ‘doctor-bladed’ on molybdenum foil used as a conductive substrate (thickness 0.1 mm, MTI Corp.) and dried in a vacuum oven at 120$^{\circ}$C for 12 hours to adhere the slurry on the substrate and evaporate the solvent.
-Specific loading of the materials ranged from 11-12 mg cm$^-{^2}$.
+Specific loading of the materials ranged from 11-12 mg cm$^{-2}$.
+
 \subsection{Electrolyte preparation}
-Anhydrous AlCl$_3$ (Sigma-Aldrich) and EMImCl (97$\%$, Sigma-Aldrich) were mixed in a molar ratio of 1.3:1, at room temperature.
-EMImCl was baked in vacuum for 24 hours at 100°C to remove residual moisture.
+Anhydrous \ce{AlCl3} (Sigma-Aldrich) and EMImCl (97$\%$, Sigma-Aldrich) were mixed in a molar ratio of 1.3:1, at room temperature.
+EMImCl was baked in vacuum for 24 hours at 100$^{\circ}$C to remove residual moisture.
 Small aliquots of AlCl$_3$ was added to EMImCl after every few minutes.
@@
 Since the electrolyte is hygroscopic in nature, it was prepared in a N$_2$-filled glove box with <0.1 ppm H$_2$O/O$_2$.
+
 \subsection{Cell assembly}
@@
 It was seen previously that steel rods reacted with the electrolyte forming a green-colored substance on the cathode.
-Slurry coated on molybdenum foil was used as the cathode and placed at bottom of the cell.
+The slurry coated on molybdenum foil was used as the cathode and placed at bottom of the cell.
 Two glass microfibers (Grade GF/F, Whatman) were used as separators.
@@
 
-\begin{figure}[tbh!]
-  \centering
-  \includegraphics[width=\textwidth]{figures/GCDCall}
-    \caption{Chronopotentiographs (Voltage vs. Time) curves of all tested cathodes.}
-  \label{figures:GCDCall}
-\end{figure}
-\include{Supplementary}
+% What is this figure doing here in the wild?
+%\begin{figure}[tbh!]
+ % \centering
+  %\includegraphics[width=\textwidth]{figures/GCDCall}
+   % \caption{Chronopotentiographs (Voltage vs. Time) curves of all tested cathodes.}
+  %\label{figures:GCDCall}
+%\end{figure}
+
+\section{Conclusions}
+
+% Where are the conclusions?
+
+%\include{Supplementary} % This should be a separate file.
 
 \bibliographystyle{unsrt}  % Something must be wrong here....
-\bibliography{zotero_refs}
+\bibliography{thesis}
 

### 2019-12-27 Supplementary.tex
Updates from Overleaf

@@
 \documentclass{article}
-%\usepackage[utf8]{inputenc}
+\usepackage{arxiv}
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{lipsum}
+\usepackage{upgreek}
 \usepackage{graphicx}
 \usepackage[version=4]{mhchem}
-% Include section in journal if known, otherwise delete
-% \paperfield{Journal Section}
+\usepackage{gensymb}
+\usepackage{verbatim}
+\usepackage{amsmath}
+\usepackage{amssymb}
+
 \title{Carbon cathodes for rechargeable aluminium-ion batteries}
-%\corraddress{Author One PhD, Department, Institution, City, State or Province, Postal Code, Country}
-%\presentadd[\authfn{2}]{Department, Institution, City, State or Province, Postal Code, Country}
+\author{
+Shalini Divya\\
+  School of Chemical and Physial Sciences\\
+  Victoria University of Wellington\\
+  Wellington, New Zealand\\
+  \texttt{shalini.divya@vuw.ac.nz}\\
+  %% examples of more authors
+   \And
+  Thomas Nann\thanks{Corresponding author.}\\
+  School of Mathematical and Chemical Sciences\\
+  The University of Newcastle\\
+  Newcastle, NSW 2308, Australia\\
+  \texttt{thomas.nann@newcastle.edu.au}\\
+}
 
-% Include the name of the author that should appear in the running header
 \begin{document}
-
+\maketitle
 \section*{Supporting Information}
@@
 
-\begin{figure}[tbh!]
+\begin{figure}[ht!]
 \centering
-  \includegraphics[width=\textwidth]{SF/ACHsyn}
+\includegraphics[width=\textwidth]{fig/ACHsyn}
 \caption{Synthesis of activated carbon from human hair using NaOH as the activating agent.}
-  \label{SF:ACHsyn}
+\label{fig:ACHsyn}
 \end{figure}
-\begin{figure}[tbh!]
+
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=\textwidth]{SF/CFExsol}
+\includegraphics[width=\textwidth]{fig/CFExsol}
 \caption{Synthesis of activated carbon from human hair using NaOH as the activating agent.
 The choice of temperature and activating agent plays a crucial role in determining pore size of the activated carbon.}
-  \label{SF:CFExsol}
+\label{fig:CFExsol}
 \end{figure}
-\begin{figure}[tbh!]
+
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=0.5\textwidth]{SF/keratin}
+\includegraphics[width=0.5\textwidth]{fig/keratin}
 \caption{Keratin: a protein abundantly found in human hair contains C-O, C=O, C-NH$_2$ bonds.}
-    \label{SF:keratin}
+\label{fig:keratin}
 \end{figure}
@@
 %\end{figure}
-\begin{figure}[tbh!]
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=\textwidth]{SF/XPSoverall}
+\includegraphics[width=\textwidth]{fig/XPSoverall}
 \caption{Overall spectra of ACH (blck), hemp fibers (blue), CFEx (green) and SUper-P(red).}
-  \label{SF:XPSoverall}
+\label{fig:XPSoverall}
 \end{figure}
-\begin{figure}[tbh!]
+
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=\textwidth]{SF/hair50mVs}
-    \caption{Cyclic voltammogram of ACH at a scan rate of 50 mV/s in a two electrode setup against \ce{Al3+}/Al showing a capacitor-like behaviour with no visible oxidation-reduction peaks unlike Figure \ref{figures:CV}b where we distinctly observed redox peaks.}
-  \label{SF:hair50mVs}
+\includegraphics[width=\textwidth]{fig/hair50mVs}
+\caption{Cyclic voltammogram of ACH at a scan rate of 50 mV/s in a two electrode setup against \ce{Al3+}/Al showing a capacitor-like behaviour with no visible oxidation-reduction peaks unlike Figure \ref{fig:CV}b where we distinctly observed redox peaks.}
+\label{fig:hair50mVs}
 \end{figure}
-\begin{figure}[tbh!]
+
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=\textwidth]{SF/PEEK}
+\includegraphics[width=\textwidth]{fig/PEEK}
 \caption{A custom-made two-electrode polyetherether ketone (PEEK) cell used for galvanostatic cycles and cyclic voltammetry.}
-  \label{SF:PEEK}
+\label{fig:PEEK}
 \end{figure}
+
 \end{document}

### 2019-12-27 manuscript.tex

@@
 \usepackage{graphicx}
-\usepackage{setspace}
-\usepackage{tgtermes}
-\usepackage{subfig}
+%\usepackage{setspace}
+%\usepackage{tgtermes}
+%\usepackage{subfig}
 \usepackage[version=4]{mhchem}
 \usepackage{threeparttable}
-\onehalfspacing
-\graphicspath{figures/}
 \usepackage{array, booktabs}
@@
 These materials differ in their general structure, porosity and morphology.
-The fullerenes display a crystalline structure, whereas hemp fibers, Super-P and ACH are amorphous in nature.
-Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$.
-Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively.
+The fullerenes display a crystalline structure, whereas hemp fibers, SPCB and hair are amorphous in nature.
+Of all materials, activated carbon from human hair recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$.
+Both hemp fibers and SPCB achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively.
 CFEx recorded its highest capacity at 78 mAh g$^{-1}$ and maintained it for 50 cycles.
@@
 Graphite, with its layered structure turned out to be an ideal intercalation cathode material \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}.
-Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}.
-Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium.
-Thus, they offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}.
+Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011-2}.
+Non-aqueous aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium.
+They offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}.
 In this work, we tested a number of rechargeable AIBs using an ionic liquid electrolyte with different carbon-based cathodes.
@@
 
-Graphite has been commonly used as a cathode in AIBs.
-It has a layered structure that enhances the intercalation process, good conductivity, and a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V.
-Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$.
+Graphite has been repeatedly used as a cathode in AIBs.
+It has (i) a layered structure that enhances the intercalation process, (ii) good conductivity, and (iii) a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V.
+Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional (3D) graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$.
 The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge.
-X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}.
-Raman data showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation.
+X-ray diffraction (XRD) and Raman spectroscopy studies helped in establishing this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017,lin_ultrafast_2015-3} as shown in Figure \ref{fig:graphitemech}.
+For example: a Raman spectra showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation.
 XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
 
-\begin{figure}[tbh!]
+\begin{figure}[h!]
   \centering
-  \includegraphics[width=\textwidth]{SF/graphitemech}
-    \caption{Intercalation of \ce{AlCl4-} ions while cell charging and deintercalation during discharge in a Al/graphite cell. The interlayer distance between two graphite sheets is 3.3 \AA.}
-  \label{SF:graphitemech}
+  \includegraphics[width=\textwidth]{fig/graphitemech}
+    \caption{Intercalation of \ce{AlCl4-} ions during charging and deintercalation during discharging in an Al/graphite cell. The interlayer distance between two graphite sheets is 3.3 \AA.}
+  \label{fig:graphitemech}
 \end{figure}
@@
 In this study, we compared four carbon-based materials with carbonised natural products.
-Super-P carbon has been used consistently as an additive to overcome conductivity loss in the active electrode material (for example, when a polymer binder such as polyvinylidene fluoride (PVDF) is added to it).
-Using it as an active material, we tried to find if Super-P contributes any capacity of its own to the battery's specific capacity.
+Super-P has been the premium choice for a carbon additive, while preparing a slurry, as it improves the conductivity of the active material.
+Using it as an active material, we tried to find if Super-P adds any capacity of its own to the battery's specific capacity.
 Activated carbon from natural products like rice or wood have been previously used in super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}.
-Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes.
-The pores absorb the charge carriers reversibly on their surface.
-Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes.
+Also known as 'hierarchical porous carbons', these structures contain pores of various sizes (mesopores and micropores), which enhance the surface area of the electrodes.
+The pores absorb the charge carriers reversibly on their surface by faradaic/ non-faradaic processes.
+Based on this hypothesis, we tested activated carbon from human hair and hemp fibers as cathodes for non-aqueous AIBs.
 
@@
 
-\begin{table}[tbh!]
-\caption{Comparing average battery metrics of carbon cathodes} \label{table1}
+\begin{table}[h!]
+\caption{Comparing battery metrics of all carbon-based cathodes tested in this work} \label{table1}
 \begin{center}
@@
 
-\begin{figure}[tbh!]
+\begin{figure}[h!]
   \centering
-  \includegraphics[width=\textwidth]{figures/CDCall}
-    \caption{Specific capacities in the a) 1$^{st}$ and b) 50$^{th}$ cycle of human hair, hemp fiber, CFEx and SPCB cathodes at a current rate of 50 mA g$^{-1}$.
-c) Cell efficiencies of cells at a current rate of 50 mAg$^{-1}$.
-d) Specific capacities of carbon cells at current rates of 25 mAg$^{-1}$, 50 mAg$^{-1}$ and 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al.
-}
-  \label{figures:CDCall}
+  \includegraphics[width=\textwidth]{fig/CDCall}
+    \caption{Specific capacities of AC (human hair, hemp fibers), CFEX and SPCB in their a) first and b) 50$^{th}$ cycle at a current rate of 50 mA g$^{-1}$.
+c) Coulombic efficiencies of cells at a current rate of 50 mAg$^{-1}$.
+d) Galvanostatic charge/discharge profile of all cells at various current rates ranging from 25 mAg$^{-1}$ to 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al.}
+  \label{fig:CDCall}
 \end{figure}
 
-Our battery system comprised a cathode, 99\% pure aluminium foil as an anode, and a room temperature ionic liquid (RTIL) acting as the electrolyte.
-ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra confirmed the presence of a few graphitic planes.
-Any number of graphite-like layers would allow \ce{AlCl4-} ions to intercalate when the cell was charged.
-However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had crystalline character.
-Intercalation of aluminium into the fullerene cages was not observed.
-We suggest that \ce{AlCl4-} anions migrated through the gaps present in between fullerenes without altering the molecular structure.
-Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{figures:CDCall}a and b).
-Structural changes in the cathode before and after the cycles were studied using Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.
+The battery system comprised a cathode, 99\% pure aluminium foil as the anode, and a room temperature ionic liquid (RTIL) as the electrolyte.
+Activated carbon derived from human hair and hemp fibers, and SPCB have a non-crystalline structure, however their Raman spectra revealed the presence of a few graphitic planes.
+Graphitic layers would allow \ce{AlCl4-} ions to intercalate during charging.
+CFEx (a mixture of \ce{C60} and \ce{C70} fullerenes) does not have a layered structure.
+Both fullerenes have a cage-like morphology and the chloroaluminates are not small enough to move in and out of them during charge/discharge.
+We suggest that \ce{AlCl4-} anions migrated through the gaps present in between the fullerenes without altering its molecular structure.
+Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{fig:CDCall}a and b).
+Morphology of the cathodes before and after the cycles were studied using Raman spectroscopy, X-ray diffraction (XRD) patterns and scanning electron microscopy (SEM).
 
-Figure \ref{figures:CDCall}a and b compares the specific capacities of all cells recorded in their 1$^{st}$ and 50${^th}$ cycles.
-Cells made of human hair displayed the highest capacity at around 100 mAh g$^{-1}$ with a coulombic efficiency at $\sim$95$\%$.
-High surface area due to the porous structure of the materials might have led to a additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}.
-Hemp cells displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles.
-CFEx cells displayed a capacity of around 80 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\%.
-With an initial capacity of 84 mAh g$^{-1}$, specific capacity of SPCB cells decreased to 47 mAh g$^{-1}$ and a low coulombic efficiency at around 40\% was recorded.
+Figure \ref{fig:CDCall}a and b compares the specific capacities of all cells for their first and 50$^{th}$ cycles.
+Human hair cathodes exhibited a high capacity of $\sim$100 mAh g$^{-1}$ with coulombic efficiency of $\sim$95$\%$.
+High surface area due to its porous structure might have led to an additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}.
+Hemp batteries displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles.
+CFEx displayed a capacity of around 80 mAh g$^{-1}$ with coulombic efficiency of $\sim$90\%.
+With an initial value of 84 mAh g$^{-1}$, specific capacity of SPCB decreased to 47 mAh g$^{-1}$ with a low coulombic efficiency of $\sim$40\%.
 Capacity for SPCB and hemp cells decreased considerably after repeated charge/discharge cycles.
-A low coulombic efficiency (observed in both hemp and SPCB cells) can be attributed to parasitic reactions of the battery.
-These can include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes}.
+A low coulombic efficiency (observed in both hemp and SPCB) can be attributed to side reactions in a battery.
+These may include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes_understanding_2015-1}.
 However, capacity fade for CFEx and human hair cells was minimal.
-This suggest that CFEx and human hair have a more stable structure compared to hemp and SPCB and they store charge reversibly \cite{pramanick}.
+This suggests that CFEx and human hair have a more stable structure and have the potential to store charge reversibly \cite{pramanick_human_2016}.
 
@@
 You need to re-write this in a more general manner.
-
-The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonized precursor.
-Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas}.
-Using alkali hydroxides, such as sodium and potassium hydroxide at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}.
+\fbox{\begin{minipage}{46.5em}
+\section*{Activation of carbon}
+The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonised precursor.
+Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas_effect_2004}.
+Using alkali hydroxides at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}.
 In this work, sodium hydroxide (NaOH) was used as the activating agent.
-The reaction that takes place inside the matrix after adding NaOH is:
+The reaction that takes place inside the carbon matrix after adding NaOH is as follows:
 
 \begin{center}
-    4NaOH + C $\longrightarrow$ 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{satish}
+    4NaOH + C $\longrightarrow$ 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{satish_macroporous_2015}
 \end{center}
 
-NaOH was reduced to free metal, Na, these atoms in turn expanded the carbon matrix after intercalating into the carbon structure.
-Increased temperature ($\sim$900$^{\circ}$ C) forces the  atoms out of the carbon matrix, thus creating micropores.
-Oxidation of carbon from oxygen atoms of the hydroxide group forms \ce{CO2} providing routes for channeling the Na atoms into the internal structure leading to well-connected porous structure \cite{satish}.
+In this reaction, NaOH was reduced to free metal, Na.
+These atoms in turn expanded the carbon matrix after intercalating into the carbon structure.
+Increased temperature (750$^{\circ}$ C) forced the  atoms out of the carbon matrix, thus creating micropores.
+Oxidation of carbon from oxygen atoms of the hydroxide group formed carbon dioxide (\ce{CO2}), providing routes for channeling the sodium atoms into the internal structure, resulting in a well-connected porous structure \cite{satish_macroporous_2015}.
 The calcinating temperature used here was 750$^{\circ}$ C.
-Figure \ref{SF:ACHsyn} displays the flowchart for activated carbon synthesis.
+Figure \ref{fig:ACHsyn} displays a flowchart describing activated carbon synthesis.
+\end{minipage}}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=\textwidth]{fig/ACHsyn}
+\caption{Synthesis of activated carbon (AC) from human hair using NaOH as the activating agent.}
+\label{fig:ACHsyn}
+\end{figure}
 
@@
 When you write, always have your worst scientific enemy in mind and write it so that you win.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.75\textwidth]{fig/CFExsol}
+\caption{Comparison of solubility of a) pure \ce{C60} fullerene b) fullerene extract (CFEx) and AC derived from hemp fibers in \ce{AlCl3}/EMImCl ionic liquid electrolyte.}
+\label{fig:CFExsol}
+\end{figure}
 
-Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals diameter of 11 \AA in a single crystal.
-However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}.
+Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals (vdW) diameter of 11\AA\ in a single crystal.
+However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}.
 They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}.
@@
 The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box.
-CFEx seemed to dissolve in our electrolyte (Figure \ref{SF:CFExsol} since no phase separation was observed.
-It has been reported that poly-sulphides formed during cycling in a lithium-sulfur battery, are soluble in the electrolyte.
+CFEx seemed to dissolve in the RTIL (Figure \ref{fig:CFExsol}) since no phase separation was observed.
+It has been reported that poly-sulphides (formed during charge/discharge cycles) are soluble in the electrolyte of a Li-S battery.
 They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}.
-Since no such effect was observed in aluminium-fullerene cells, this phenomena does not seem to impact the charge-storing capacity of CFEx.
-On the contrary, the cells displayed excellent capacity retention at various current rates(Figure \ref{figures:CDCall}d).
+Since no such effect was observed in aluminium-fullerene cells, the solubility of fullerenes does not seem to impact the charge-storing capacity of CFEx.
+On the contrary, aluminium-fullerene batteries demonstrated excellent capacity retention at various current rates(Figure \ref{fig:CDCall}d).
+
+ \begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{fig/superPmech}
+    \caption{Suggested mechanism for an aluminium-SPCB cell.
+\ce{AlCl4-} anions intercalate into the very few graphitic planes in Super-P, while few anions adsorb onto its surface.
+However, further cycling leads to cathode pulverisation, which results in capacity fading.}
+  \label{fig:superPmech}
+\end{figure}
+
+Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure.
+The pore sizes range from $\sim$30-50 nm \cite{younesi_analysis_2015}.
+As a cathode material, SPCB underwent the highest capacity loss within 30 cycles (45\%).
+It seems continuous cycling destroyed the structural arrangement of the carbon atoms, which resulted in further alleviated capacity and low coulombic efficiencies.
+
+ \begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{fig/hempmech}
+    \caption{Suggested mechanism for an aluminum-hemp cell.
+Hemp fibers have pore sizes which might be as large as 2.0-2.5 $\mu$m allowing the \ce{AlCl4-} to get absorbed on their surface.
+However, agglomeration of these fibers after a few cycles reduces the number of active sites available for effective charge storage.}
+  \label{fig:hempmech}
+\end{figure}
+
+ \begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{fig/raman}
+    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx, b) hemp, c) human hair and d) SPCB cathodes displaying presence of both D and G bands.}
+  \label{fig:raman}
+\end{figure}
+
+It has been previously established that chloroaluminates intercalate into the graphitic planes during charging \cite{lin_ultrafast_2015-3}.
+Since activated carbon and SPCB cathodes tested in this work have graphitic planes present in them, we compared the pristine and charged electrodes only.
+Figure \ref{fig:raman} displays the Raman spectra of the pristine and charged (intercalated) cathodes.
+Pristine hair, hemp and SPCB cathodes had a significant D-band present in them, indicating absence of an ordered structure (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB).
+Broad peaks at about 1600 cm$^{-1}$ and about 1350 cm$^{-1}$ arise from \ce{sp2} clusters like $\alpha$-carbons with bond angle disorder \cite{shimo}.
+Raman spectra of CFEx in Figure \ref{fig:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules.
+A 'pentagonal pinch mode', usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$.
+\ce{C70} has multiple bands because it has a reduced molecular symmetry, which increases the number of vibrational modes, consequently increasing the number of active Raman bands \cite{kimbrell_analysis_2014}.
+It was interesting to note that the spectra of charged CFEx looked strikingly similar to the pristine ones, Figure \ref{fig:raman}c.
+Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the fullerenes did not undergo any significant structural change during cycles.
+Charged AC (from hair) cathodes showed an increased full-width at half maxima (FWHM), which suggested an increase in the lattice defects and structure deformities.
+Obviously, these defects arise after intercalation of chloroaluminates into the few graphitic planes present in the carbon matrix.
+Furthermore, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}.
+Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge \cite{brezesinski_ordered_2010}.
+Schematic of an aluminium-hair battery is illustrated in Figure \ref{fig:ACHmech}.
+
+ \begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{fig/ACHmech}
+    \caption{Suggested mechanism for an aluminium-human hair cell.
+Chloroaluminates (\ce{AlCl4-}) intercalate into the few graphitic planes and micro/mesopores present in them, in addition to surface adsorption of ions displaying both Faradaic and non-Faradaic processes for charge storage.}
+  \label{fig:ACHmech}
+\end{figure}
+
+%contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.  
+Hemp fibers and SPCB had a highly disordered structure to begin with.
+Repeated intercalation or absorption of ions on their surface in the first few cycles would have further increased the lattice defects, which is one of the reasons why hemp and SPCB batteries failed to retain their capacity.
+However, CFEx does not have graphitic planes to intercalate chloroaluminate ions.
+Since the fullerenes have a very high surface area, surface adsorption of ions is highly likely \cite{adams_van_1994}.
+Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes (as shown in Figure \ref{fig:CFExmech}) and for the surface-based redox processes to take place in a systematic way.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/superPmech}
-    \caption{Suggested mechanism for a \textbf{Al/Super-P} cell.
-Super-P has a very amorphous structure with a few graphite-like planes present in it.
-\ce{AlCl4-} ions intercalate into those layers and give the cell its capacity.
-However, cathode pulverisation results in capacity fading.}
-  \label{figures:superPmech}
+  \includegraphics[width=\textwidth]{fig/CFExmech}
+    \caption{Suggested mechanism for a fullerene cell. \ce{AlCl4-} ions seeping in through the gaps present between fullerene molecules.}
+  \label{fig:CFExmech}
 \end{figure}
 
-Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure.
-Its pore size ranges from $\sim$30-50 nm \cite{younesi_analysis_2015}.
-SPCB has the least graphitic structure if compared to human hair and hemp fibers.
-It seems continuous cycling might have destroyed the arrangement of the carbon atoms, which resulted in poor capacity retention and low coulombic efficiencies.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.8\textwidth]{fig/SEM}
+    \caption{Scanning electron microscopy (SEM) images comparing pristine a) human hair, b) hemp, c) CFEx and d) SPCB and charged e)human hair, f) hemp, g) CFEx and h) SPCB cathodes.
+Hemp fibers and SPCB undergo permanent changes after charge/discharge cycles and fail to retain capacity.}
+  \label{fig:SEM}
+\end{figure}
+
+Figure \ref{fig:SEM} shows the SEM images of pristine (Figure \ref{fig:SEM}a, b, c and d) and charged (\ref{fig:SEM}e,f,g and h) cathodes of all carbon materials.
+Activated carbon has a highly porous structure as seen in Figure \ref{fig:SEM}b and d).
+However, hemp cathodes lost their porosity and degraded after 30 cycles, Figure \ref{fig:SEM}f).
+Significant agglomeration was observed in SPCB as well (Figure \ref{fig:SEM}d) and h).
+It was interesting to note that the cycled AC (from hair) and fullerene cathodes did not undergo any significant changes after cycles.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{fig/XRD}
+    \caption{X-ray diffarction patterns of a) CFEx and b)human hair cathodes to study changes in their lattice after galvanostatic cycles in a two-electrode setup against \ce{Al$^{3+}$/Al} with characteristic peaks marked for \ce{C60} (in grey boxes) and \ce{C70} (in blue inverted trainagles).}
+  \label{fig:XRD}
+\end{figure}
+
+To further explore the structural stability and the mechanism in CFEx and hair batteries, X-ray diffraction patterns were examined.
+Pristine (in black), charged (in green) and discharged (in red) cathodes of CFEx and human hair are showed in Figure \ref{fig:XRD}a and b respectively.
+Figure \ref{fig:XRD}a displayed the characteristic peaks of both \ce{C60} and \ce{C70} at 2$\theta$ values of 10.9$^{\circ}$, 17.8$^{\circ}$, 20.9$^{\circ}$ and 28.2$^{\circ}$ for \ce{C60} and 18.9$^{\circ}$, 19.3$^{\circ}$ and 21.8$^{\circ}$ for \ce{C70} molecules.
+New diffraction peaks at lower 2$\theta$ values appeared for charged electrodes.
+However, after discharge, the XRD patterns looked similar to the diffraction peaks of the pristine cathode.
+This data strongly suggests a reversible process taking place during cycles.
+To confirm, we calculated the unit cell lattice parameters for both pristine and charged cathodes for a \ce{C60} molecule.
+The unit cell had a tetragonal crystal system with space group of P42/ mmc and a space group number 131 (ICDD: 04-013-1339).
+Lattice parameters 'a' and 'b' for the charged cathode increased from 9.06 \AA\ to 9.57 \AA\ and 'c' increased from 15.03 \AA\ to 15.65 \AA, as shown in Figure \ref{fig:CFExcryst}a and b.
+Lattice parameters of a discharged fullerene were closer to pristine values.
+These changes suggested a reversible insertion of chloroaluminates into the free spaces between fullerene molecules taking place.
+A possible site for \ce{AlCl4-} intercalation is depicted in Figure \ref{fig:CFExcryst}c.
+XRD patterns of human hair cathodes were inconclusive (Figure \ref{fig:XRD}b).
+Pristine cathode showed broad peaks that demonstrate an amorphous and highly porous structure.
+However, the material became more symmetrical and crystalline after cycles.
+Charged and discharged cathodes exhibited similar looking patterns implying no change in the newly formed crystal lattice during cycles.
+It is to be noted that presence of crystallinity in an active material does not limit the surface-based charge storing capacity \cite{kim_synthesis_2006, jow_factors_2018}.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/hempmech}
-    \caption{Suggested mechanism for a \textbf{Al/hemp} cell.
-The fibers have a large pore size (2.0-2.5 $\mu$m) which allow the \ce{AlCl4-} to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
-  \label{figures:hempmech}
-\end{figure}
-
- \begin{figure}[tbh!]
-  \centering
-  \includegraphics[width=\textwidth]{figures/raman}
-    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx , b) hemp fibers, c) ACH and d) Super-P cathodes indicating presence of both D and G-bands.}
-  \label{figures:raman}
-\end{figure}
-
-In aluminum-graphite cells, it has been established that \ce{AlCl4-} ions intercalate while charging \cite{lin_ultrafast_2015}.
-Since the materials we tested have graphitic planes present, we focused our analysis on the pristine and charged electrodes.
-Figure \ref{figures:raman} displays Raman spectra of the tested cathodes.
-Pristine human hair, hemp fibers and SPCB had a significant D-band present indicating absence of an ordered structure with presence of lattice defects and deformities (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB).
-Figure \ref{figures:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules.
-The 'pentagonal pinch mode', which is usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$.
-However, \ce{C70} has multiple bands.
-Reduction in its molecular symmetry increases the number of vibrational modes, thus increasing the active Raman bands \cite{kimbrell_analysis_2014}.
-Pristine CFEx cathode was composed of both \ce{C60} and \ce{C70} Raman bands as seen in Figure \ref{figures:raman}c.
-It was interesting to note that charged CFEx cathodes looked strikingly similar.
-Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the structure remained intact after cycles.
-Human hair has a high surface area and an inter-connected mesoporosity.
-The charged cathodes showed a higher FWHM which suggests an increase in the lattice defects.
-Obviously, these defects arise after intercalation of chloroaluminates; it is assumed that these ions intercalate into the few graphitic planes present in the carbon matrix.
-In addition, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}.
-Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge\cite{brezesinski_ordered_2010}.
-A schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}.
-%contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.  
-Hemp fibers and SPCB had fewer graphitic planes and a highly disordered structure to begin with.
-The lattice defects seemed to increase after galvanostatic cycles.
-Continuous intercalation or absorption of ions on their surface would have further destroyed the cathode structure.
-This might be the reason why hemp and SPCB cells failed to retain capacity after a few cycles.
-However, CFEx does not have graphitic planes.
-It consists of a bunch of \ce{C60} and \ce{C70} fullerenes.
-Insertion of \ce{AlCl4-} ions inside the cage-like structure would be thermodynamically impossible.
-Since the fullerenes have a very high surface area, surface adsorption of ions is likely \cite{adams}.
-Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes \ref{figures:CFExmech}.
-Capacity retention of the aluminium-CFEx cells suggests that the interaction between the fullerenes and \ce{AlCl4-} ions takes place in a systematic way.
-
-\begin{figure}[tbh!]
-  \centering
-  \includegraphics[width=\textwidth]{figures/SEM}
-    \caption{Scanning electron microscopy images comparing pristine a) ACH, b) hemp fibers, c) CFEx and d) Super-P; and charged e)ACH, f) hemp fibers, g) CFEx and h) Super-P electrodes.
-Hemp fibers and Super-P undergo prominent changes after charge/discharge cycles (visible agglomeration of carbon atoms).}
-  \label{figures:SEM}
-\end{figure}
-
-In Figure \ref{figures:SEM}, we compared the SEM images of pristine (Figure \ref{figures:SEM}a, b, c and d) and charged (\ref{figures:SEM}e,f,g and h) cathodes of all tested materials.
-Hemp and SPCB had a porous structure (Figure \ref{figures:SEM}b and d) to begin with, which degraded after a few cycles (Figure \ref{figures:SEM}f and h).
-Significant agglomeration occurred in hemp and SPCB cathodes after continuous cycling.
-
-\begin{figure}[tbh!]
-  \centering
-  \includegraphics[width=\textwidth]{figures/XRD}
-    \caption{XRD spectra comparing a pristine (black), charged (green) and discharged (red) a) CFEx and b)ACH cathode to study changes in their lattice after 50 galvanostatic cycles in a two-electrode setup against \ce{Al$^{3+}$/Al} with characteristic peaks marked for \ce{C60} (in grey) and \ce{C70} (in blue).}
-  \label{figures:XRD}
-\end{figure}
-
-To fully understand the mechanism in CFEx and human hair, we examined their XRD spectra in Figure \ref{figures:XRD}.
-Pristine, charged and discharged cathodes of CFEx and human hair were compared in Figure \ref{figures:XRD}a and b respectively.
-Pristine cathodes displayed the characteristic peaks of both \ce{C60} and \ce{C70} at 2$\theta$ values of 10.9$^{\circ}$, 17.8$^{\circ}$, 20.9$^{\circ}$ and 28.2$^{\circ}$ for \ce{C60} and 18.9$^{\circ}$, 19.3$^{\circ}$ and 21.8$^{\circ}$ for \ce{C70} molecules.
-Charged electrodes displayed new diffraction peaks at lower 2$\theta$ values.
-However, after discharge, the XRD pattern resembled the pristine cathode.
-This data strongly suggests a reversible process.
-To confirm, we calculated the unit cell lattice parameters for both pristine and charged cathodes for a \ce{C60} molecule.
-The unit cell had a tetragonal crystal system with space group of P42/mmc and a space group number 131 (ICDD: 04-013-1339 for \ce{C60}).
-Lattice parameter 'a' and 'b' for the charged electrode changed from 9.06 \AA to 9.57 \AA .
-Lattice parameter 'c' changed from 15.03 \AA to 15.65 \AA, in Figure \ref{figures:CFExcryst}a and b.
-Lattice parameters for discharged cathode were closer to pristine values.
-These changes suggested a reversible intercalation process taking place.
-A possible site for \ce{AlCl4-} intercalation is depicted in Figure \ref{figures:CFExcryst}c.
-XRD spectra for human hair cathodes was inconclusive (Figure \ref{figures:XRD}b).
-Pristine cathode showed broad peaks suggesting an amorphous and highly porous structure.
-However, the material became more ordered after cycles.
-Charged and discharged cathodes have similar patterns which means no structural changes took place in aluminium-hair batteries.
-Also, presence of crystallinity in an active material does not limit the surface-based charge storage \cite{kim_synthesis_2006, jow_factors_2018}.
-So, we hypothesise that human hair followed a capacitor-like behaviour after intercalation of ions in the initial cycles.
-
- \begin{figure}[tbh!]
-  \centering
-  \includegraphics[width=\textwidth]{figures/ACHmech}
-    \caption{Suggested mechanism for an aluminium-human hair cell.}
-  \label{figures:ACHmech}
-\end{figure}
-
-\begin{figure}[tbh!]
-  \centering
-  \includegraphics[width=\textwidth]{figures/CFExcryst}
+  \includegraphics[width=\textwidth]{fig/CFExcryst}
     \caption{Changes in the lattice parameters of a \ce{C60} unit cell.
@@
 c) Expected intercalation sites of \ce{AlCl4-} ions in the unit cell.}
-  \label{figures:CFExcryst}
+  \label{fig:CFExcryst}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/XPSC}
+  \includegraphics[width=\textwidth]{fig/XPSC}
     \caption{Carbon 1s XPS spectra of pristine a) ACH, b) Super-P, c) hemp fibers and d) CFEx cathodes.While ACH, Super-P and hemp fibers observe carbonyl functional groups, CFEx cathodes have symmetrical looking $\pi$* and $\sigma$* satellite peaks.}
-  \label{figures:XPSC}
+  \label{fig:XPSC}
 \end{figure}
 
-We observed XPS spectra of all pristine cathodes to understand their composition.
-Human hair, hemp fibers and SPCB had similar looking peaks for carbon 1s orbital as shown in figure \ref{figures:XPSC}.
-Binding energies suggesting sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds (formed between the binder and active material) appeared in hair, hemp fibers and SPCB cathode spectra.
-Hair is mainly composed of a protein called keratin displayed in Figure \ref{SF:keratin} and the multiple chemical environments of carbon in Figure \ref{figures:XPSC}a) are derived from Keratin.
+XPS spectra of carbon 1s orbital of all pristine cathodes is shown in Figure \ref{fig:XPSC}.
+Hair, hemp fibers and SPCB had similar looking peaks for the 1s orbital.
+All three cathodes displayed peaks for sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds .
+Since hair is mainly composed of a protein called keratin (Figure \ref{fig:keratin}), it can be deduced that multiple chemical environments of carbon, shown in Figure \ref{fig:XPSC}a), are derived from Keratin.
 Sulphide bonds are an essential part of this protein and a C-S binding energy is observed at 286.94 eV (blue peak).
+
+\begin{figure}[th!]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/keratin}
+\caption{Keratin: a protein abundantly found in human hair contains C-O, C=O, C-NH$_2$ bonds.}
+\label{fig:keratin}
+\end{figure}
 
@@
 
-Functional groups that contain oxygen, such as carbonyl and ester groups, improve the wettability of a material and increases the availability of active surface area \cite{younesi_analysis_2015}.
-SPCB is produced from partial oxidation of petrochemical precursors and exhibits a large specific surface area with a very high electrical conductivity \cite{gnanamuthu_electrochemical_2011}.
-A perfect graphite surface containing only carbon atoms, without heteroatoms like oxygen and sulfur would give a very well-ordered structure.
-Presence of impurities such as carbonyl groups creats defects resulting in a less graphitic and more amorphous structure\cite{hao_carbonaceous_2013}.
-XPS spectra for CFEx electrodes was uniquely different with highly symmetrical peaks.
-The presence of $\pi$ electrons on the fullerene's surface results in  multiple $\pi$ satellite peaks.
-These peaks are characteristic signs of a \ce{C60} molecule \cite{skryleva_xps_2016}.
-The symmetrical peaks appear in both high (in green) and low energy ranges (in red, 284–289 eV)\cite{erbahar_spectromicroscopy_2016, poirier_carbon_1993}.
+Functional groups that contain oxygen, such as carbonyl and ester groups, improve the wettability of a material, which increases the availability of active surface area \cite{younesi_analysis_2015}.
+SPCB is produced from partial oxidation of petrochemical precursors \cite{gnanamuthu_electrochemical_2011}.
+A perfect graphite surface containing only carbon atoms, without heteroatoms like oxygen and sulfur, would give a very well-ordered structure.
+Presence of impurities such as carbonyl groups creates defects resulting in a less graphitic and more amorphous structure\cite{hao_carbonaceous_2013} and peaks at 288.0 eV in AC and SPCB cathodes confirm that.
+Spectra for C 1s orbital of CFEx was uniquely different than the others due to presence of several highly symmetrical peaks.
+The presence of $\pi$ electrons on its surface results in  multiple $\pi$ satellite peaks, which are typical in a \ce{C60} molecule \cite{skryleva_xps_2016}.
+These peaks appear in both high (in green) and low energy ranges (in red) \cite{erbahar_spectromicroscopy_2016, poirier_carbon_1993}.
 %Existence of several peaks in the $\pi$ satellite of a C$_6_0$ molecule is caused by the angular quantisation of orbitals around the centre of the spherical molecule. 
@@
 
-\begin{figure}[tbh!]
+\begin{figure}[h!]
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/XPSON}
+  \includegraphics[width=0.8\textwidth]{fig/XPSON}
     \caption{XPS spectra of O 1s orbital for a) human hair, b) hemp fibers c) CFEx and d) SPCB cathodes.
@@
 Human hair displayed distinct binding energies for pyridinic and pyrrolic N-species; hemp fibers, CFEx and SPCB had smaller amounts of surface proteins.}
-  \label{figures:XPSON}
+  \label{fig:XPSON}
 \end{figure}
 
-Figure \ref{figures:XPSON}a-d shows various binding energies for O 1s orbital.
-As mentioned earlier, oxygen-containing functional groups enhance the wettability of a material and presence of oxygen atoms make redox reactions feasible \cite{li_effect_2011, oh_oxygen}.
-Oxygen-containing surface functional groups can provide pseudo-capacitance by reacting with electrolyte ions \cite{bleda_martinez}.
-This might be one of the reasons why aluminium-hair and aluminium-fullerene batteries performed better than others.
+Figure \ref{fig:XPSON}a-d shows various binding energies for O 1s orbital.
+In addition to enhancing the wettability of a material, oxygen containing functional groups make redox reactions feasible \cite{li_effect_2011, oh_oxygen_2014}.
+Oxygen-containing surface functional groups can provide pseudo-capacitance by reacting with electrolyte ions \cite{bleda-martinez_role_2005}.
+This might another reason why aluminium-hair batteries performed better than the others.
+Figure \ref{fig:XPSoverall} displays the overall spectra of all tested cathodes.
+Table \ref{table2} compiles all the functional groups with their respective binding energies for all tested cathode materials in this work.
 
- \begin{figure}[tbh!]
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=\textwidth]{figures/CV}
+\includegraphics[width=\textwidth]{fig/XPSoverall}
+\caption{Overall spectra of human hair (black), hemp fibers (blue), CFEx (green) and Super-P(red).}
+\label{fig:XPSoverall}
+\end{figure}
+
+ \begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{fig/CV}
     \caption{Cyclic voltammograms of a) CFEx, b) ACH, c) Super-P and d) hemp fibers cathodes at a scan rate of 10 mV s$^{-1}$ against \ce{Al3+}/Al as a counter/reference electrode in a two-electrode setup.
 ACH cathode observed a larger CV area than other cathodes, which comes from an additional pseudocapacitance, adding capacity to the system.}
-  \label{figures:CV}
+  \label{fig:CV}
 \end{figure}
 
-Lastly, to confirm that ACH is a psedocapacitive material, we compared cyclic voltammograms of all cathodes at a scan rate of 10 mV s$^{-1}$.
-From Figure \ref{figures:CV}a-e, it was seen that human hair had a rectangular capacitor-like CV curve.
-However, redox processes were noticeable at a lower scan rate (10 mV s$^{-1}$) and tiny redox peaks visible (Figure \ref{figures:CV}b).
-At a higher scan rate (50 mV s$^{-1}$), the redox peaks disappeared and the material displays solely a capacitor-like behaviour, shown in Figure \ref{SF:hair50mVs} \cite{guan_capacitive, dupont_separating}.
+Lastly, to confirm that AC derived from human hair is in fact a psedocapacitive material, we compared cyclic voltammograms of all cathodes at a scan rate of 10 mV s$^{-1}$.
+Figure \ref{fig:CV}a-e showed that human hair batteries demonstrated a more rectangular, capacitor-like CV curve.
+However, redox processes were noticeable at a scan rate of 10 mV s$^{-1}$ and tiny redox peaks were visible (Figure \ref{fig:CV}b).
+At a higher scan rate (50 mV s$^{-1}$), the redox peaks disappeared and the material displayed an ideal capacitor-like CV curve, shown in Figure \ref{fig:hair50mVs} \cite{guan_capacitive_2016, dupont_separating_2015}.
 
- \begin{figure}[tbh!]
+\begin{figure}[th!]
 \centering
-  \includegraphics[width=\textwidth]{figures/CFExmech}
-    \caption{Suggested mechanism for a \textbf{Al/CFEx} cell.
-\ce{AlCl4-} ions seeping in through the gaps present between fullerene molecules.
-A few \ce{AlCl4-} ions get absorbed on the cathode's surface resulting in a capacity purely from a non-Faradaic process.}
-  \label{figures:CFExmech}
+\includegraphics[width=\textwidth]{fig/hair50mVs}
+\caption{Cyclic voltammogram of ACH at a scan rate of 50 mV/s in a two electrode setup against \ce{Al3+}/Al showing a capacitor-like behaviour with no visible oxidation-reduction peaks unlike Figure \ref{fig:CV}b where we distinctly observed redox peaks.}
+\label{fig:hair50mVs}
 \end{figure}
 
-\begin{figure}[tbh!]
+\begin{figure}[h!]
   \centering
-  \includegraphics[width=\textwidth]{figures/CFExACHlong}
+  \includegraphics[width=\textwidth]{fig/CFExACHlong}
     \caption{Discharge capacities of a) ACH and b) CFEx cathodes at current rates of 50mAg$^{-1}$, 500mAg$^{-1}$, 1.0 Ag$^{-1}$ and 1.5 Ag$^{-1}$ along with their coulombic efficiencies. }
-  \label{figures:CFExACHlong}
+  \label{fig:CFExACHlong}
 \end{figure}
 
+\newpage
 % Are the following the conclusions?
 \section{Conclusion}
-ACH proved to be the best carbon-based cathode among all the tested materials, with a specific capacity of 100 mAh g$^{-1}$ at a potential of 1.9 V with a coulombic efficiency of $\sim$90$\%$.
-Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers of ACH, hemp fibers and Super-P.
-We found that CFEx lacks a layered structure and it is mainly a cluster of \ce{C60} and \ce{C70} molecules.
-\ce{AlCl4-} anions seep in and out of the gaps in between the fullerenes changing its structure during insertion and expanding the crystal lattice (Figure \ref{figures:CFExmech}).
-Since the cathode maintains its structural integrity, the coulombic efficiency remains stable throughout the cycles for CFEx cell.
-Hemp fibers and Super-P on the other hand, have a highly amorphous structure and degrades after every cycle, resulting in a low capacity value.
-Figure \ref{figures:CFExACHlong} compares the 50th cycle measurement for Al/ACH and Al/natural graphite cell.
+In summary, AC derived from human hair proved to be the best carbon-based cathode among all the tested materials in this work, with a specific capacity of 100 mAh g$^{-1}$ at a potential of 1.9 V with a coulombic efficiency of $\sim$90$\%$.
+Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers.
+We found that in CFEx \ce{AlCl4-} anions seep in and out of the gaps in between the fullerenes changing its structure and slightly expanding the crystal lattice during charging(Figure \ref{fig:CFExmech}).
+Moreover, fullerenes maintains their structural integrity and coulombic efficiency throughout the cycles.
+Hemp fibers and Super-P on the other hand, have a highly amorphous structure, which degraded after every cycle, resulting in a low capacity value.
+Figure \ref{fig:CFExACHlong} compares the 50th cycle measurement for Al/hair and Al/natural graphite cell.
 It not only displays a higher specific capacity than conventional graphite, but also a high battery voltage of 1.92 V with an energy density of 202 Wh kg$^{-1}$.
+The high battery performance can be attributed to the porosity of the material combined with high surface area and hetero-atom doping effects, combining surface-based non-Faradaic and Faradaic contributions.
+Hair based aluminium-ion batteries would not only be cheaper than state of the art, but would also be one of its kind bio-degradable materials in the battery industry.
+
+\newpage
 
@@
 \subsubsection*{Activated carbon from human hair}
+
 \subsubsection*{Activated carbon from hemp fibers}
@@
 \subsubsection*{Fullerene extract}
-C60/C70, approx. 85\% C60, 14\% C70, and 1\% higher fullerenes, was purchased from SES research and used as received.
+C60/C70, approx. 85\% \ce{C60}, 14\% \ce{C70}, and 1\% higher fullerenes, was purchased from SES research and used as received.
 \subsubsection*{Super-P carbon black}
@@
 \subsection{Cell assembly}
-PEEK (polyether ether ketone) cells were used for electrochemical measurements (Figure \ref{SF:PEEK}).
+PEEK (polyether ether ketone) cells were used for electrochemical measurements (Figure \ref{fig:PEEK}).
 Molybdenum rods were used as current collectors.
@@
 
+\begin{figure}[th!]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/PEEK}
+\caption{A custom-made two-electrode polyetherether ketone (PEEK) cell used for galvanostatic cycles and cyclic voltammetry.}
+\label{fig:PEEK}
+\end{figure}
+
 % What is this figure doing here in the wild?
@@
 
-\section{Conclusions}
-
-% Where are the conclusions?
-
-%\include{Supplementary} % This should be a separate file.
-
 \bibliographystyle{unsrt}  % Something must be wrong here....
-\bibliography{thesis}
+\bibliography{thesisref2}
 

### 2020-03-17 manuscript.tex

@@
 \begin{abstract}
- In this work, we compare four different forms of carbon: activated carbon from human hair, activated carbon from hemp fibers, a fullerene mixture consisting of \ce{C60} and \ce{C70} fullerenes (CFEx) and Super-P carbon black (SPCB) as cathodes for non-aqueous aluminium-ion batteries.
+ In this work, four different forms of carbon: activated carbon (AC) from human hair, AC from hemp fibers, a carbon fullerene extract consisting of \ce{C60} and \ce{C70} fullerene (CFEx) and Super-P carbon black (SPCB) were tested and compared as cathodes for non-aqueous aluminium-ion batteries (AIBs).
 These materials differ in their general structure, porosity and morphology.
 The fullerenes display a crystalline structure, whereas hemp fibers, SPCB and hair are amorphous in nature.
-Of all materials, activated carbon from human hair recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$.
+Of all materials, AC obtained from human hair recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a Coulombic efficiency (CE) of $\sim$90\% at a current rate of 50 mV s$^{-1}$.
 Both hemp fibers and SPCB achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively.
@@
 \section{Introduction}
-Different varieties of carbon-based materials have been widely used in energy storage applications.
-Graphite, with its layered structure turned out to be an ideal intercalation cathode material \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}.
-Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011-2}.
-Non-aqueous aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium.
-They offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}.
-In this work, we tested a number of rechargeable AIBs using an ionic liquid electrolyte with different carbon-based cathodes.
-The aim of this study was to systematically explore the properties of different carbon-materials when used as AIB cathodes.
+Non-aqueous aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium (Al) \cite{lin_ultrafast_2015-2,paranthaman_transformational_2010,wang_advanced_2017}.
+They offer an interesting potential long-term alternative to the LIB technology \cite{ambroz_trends_2017-1}.
+Different varieties of carbon-based materials have been widely used in various energy storage applications.
+Graphite, with its layered structure turned out to be an ideal intercalation cathode material for many types of ions \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}.
+It allows reversible intercalation of ions in its layers during charging and discharging processes, which results in high specific capacities.
+Owing to its porous structure, activated carbon (AC) provides a high surface area, and is a typical electrode material used in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011-2}.
+In this work, a number of rechargeable AIBs were tested using an ionic liquid electrolyte with different carbon-based cathodes.
+The aim of this study was to systematically explore the properties of different carbon materials when used as AIB cathodes.
 
-Graphite has been repeatedly used as a cathode in AIBs.
-It has (i) a layered structure that enhances the intercalation process, (ii) good conductivity, and (iii) a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V.
-Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional (3D) graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$.
-The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge.
-X-ray diffraction (XRD) and Raman spectroscopy studies helped in establishing this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017,lin_ultrafast_2015-3} as shown in Figure \ref{fig:graphitemech}.
-For example: a Raman spectra showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation.
-XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
+Graphite has been repeatedly used as a cathode in AIBs \cite{lin_ultrafast_2015-2, wang_advanced_2017,zhang_novel_2016-1, rani_fluorinated_2013} due to its layered structure that enhances the intercalation process, good conductivity, and high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V.
+Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional (3D) graphitic-foam \cite{wu_3d_2016}, graphene aerogels \cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing specific capacities ranging from 60--250 mAh g$^{-1}$.
+As per the established mechanism, \ce{AlCl4-}-anions intercalate into graphite layers when the cell is being charged and deintercalate during discharge.
+X-ray diffraction (XRD) and Raman spectroscopy studies helped in establishing this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017,lin_ultrafast_2015-2} as shown in Figure \ref{fig:graphitemech}.
+For example, Raman spectra showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation \cite{wang_advanced_2017}.
+X-ray photoelectron spectroscopy (XPS) studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.
 
-\begin{figure}[h!]
+\begin{figure}[] %[h!]
   \centering
@@
 
-In this study, we compared four carbon-based materials with carbonised natural products.
-Super-P has been the premium choice for a carbon additive, while preparing a slurry, as it improves the conductivity of the active material.
-Using it as an active material, we tried to find if Super-P adds any capacity of its own to the battery's specific capacity.
-Activated carbon from natural products like rice or wood have been previously used in super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}.
-Also known as 'hierarchical porous carbons', these structures contain pores of various sizes (mesopores and micropores), which enhance the surface area of the electrodes.
-The pores absorb the charge carriers reversibly on their surface by faradaic/ non-faradaic processes.
-Based on this hypothesis, we tested activated carbon from human hair and hemp fibers as cathodes for non-aqueous AIBs.
+In this work, four different carbon-based materials --- Ac from human hair, AC from hemp fibers, fullerene extract (CFEx) and Super-P carbon black (Super-P) were investigated as cathodes for AIBs.
+Super-P is an amorphous form of carbon.
+It is highly conductive and is added in electrode slurries to enhance the conductivity of a cathode material.
+Activated carbon derived from natural products such as rice husk, coconut shells or wood, have been previously used in batteries and super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}.
+Most of the carbon-based materials have a high surface area.
+AC derived from both hair and hemp fibers contain pores of various sizes (mesopores and micropores).
+Fullerenes on the other hand, has a tightly packed structure with Brunauer-Emmet and Teller (BET) surface area of 19 m$^2$ g$^{-1}$ \cite{}.
 
 \section{Results and discussion}
+The battery system comprised a cathode, 99\% pure Al foil as the anode, and a room temperature ionic liquid (RTIL) as the electrolyte.
+Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure \cite{see_reversible_2017}.
+The pore sizes range from $\sim$30-50 nm \cite{younesi_analysis_2015}.
+AC derived from human hair, hemp fibers, and SPCB all have a non-crystalline structure.
+However their Raman spectra revealed the presence of a few graphitic planes.
+These planes would allow \ce{AlCl4-} ions to intercalate during charging.
+CFEx (a mixture of \ce{C60} and \ce{C70} fullerenes) does not have a layered structure.
+Fullerenes have a cage-like morphology and the chloroaluminates are not small enough to move in and out of them during charge/discharge.
+We assumed that \ce{AlCl4-} anions migrated through the gaps present in between the fullerenes and interacted with their surface.
+Specific capacities and Coulombic efficiencies (CEs) of the cathodes were recorded at various current rates (cf.\ Figure \ref{fig:CDCall}a and b).
+Morphology of the cathodes before and after the cycles were studied using Raman spectroscopy, XRD patterns and scanning electron microscopy (SEM).
 
-\begin{table}[h!]
-\caption{Comparing battery metrics of all carbon-based cathodes tested in this work} \label{table1}
-\begin{center}
-\begin{tabular}{|lcccc|}
-\hline
-Active material & {\textbf{Size}} & {\textbf{Specific capacity}} & {\textbf{Cell efficiency}} & {\textbf{Cell voltage}}\\
- & {\textbf{(pore size)}} & {\textbf{(mAh g$^{-1}$)}} & {\textbf{(\%)}} & {\textbf{(V)}}\\
-\hline
-Human hair & 5${\mu}$ m & 102 & 97 & 1.9 \\
-Fullerene mix & 8.8 \AA & 78 & 85 & 1.7 \\
-Hemp fibers & 2.3 $\mu$ m & 49 & 75 & 1.8 \\
-SPCB & 300 \AA & 46 & 40 & 1.5 \\
-\hline  % Please only put a hline at the end of the table
-\end{tabular}
-\end{center}
-\end{table}
-
-\begin{figure}[h!]
+\begin{figure}[]
   \centering
   \includegraphics[width=\textwidth]{fig/CDCall}
-    \caption{Specific capacities of AC (human hair, hemp fibers), CFEX and SPCB in their a) first and b) 50$^{th}$ cycle at a current rate of 50 mA g$^{-1}$.
-c) Coulombic efficiencies of cells at a current rate of 50 mAg$^{-1}$.
+    \caption{Specific capacities of AC (human hair, hemp fibers), CFEx and SPCB in their a) first and b) 50$^{th}$ cycle at a current rate of 50 mA g$^{-1}$.
+c) Coulombic efficiencies (CEs) of cells at a current rate of 50 mAg$^{-1}$.
 d) Galvanostatic charge/discharge profile of all cells at various current rates ranging from 25 mAg$^{-1}$ to 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al.}
@@
 
-The battery system comprised a cathode, 99\% pure aluminium foil as the anode, and a room temperature ionic liquid (RTIL) as the electrolyte.
-Activated carbon derived from human hair and hemp fibers, and SPCB have a non-crystalline structure, however their Raman spectra revealed the presence of a few graphitic planes.
-Graphitic layers would allow \ce{AlCl4-} ions to intercalate during charging.
-CFEx (a mixture of \ce{C60} and \ce{C70} fullerenes) does not have a layered structure.
-Both fullerenes have a cage-like morphology and the chloroaluminates are not small enough to move in and out of them during charge/discharge.
-We suggest that \ce{AlCl4-} anions migrated through the gaps present in between the fullerenes without altering its molecular structure.
-Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{fig:CDCall}a and b).
-Morphology of the cathodes before and after the cycles were studied using Raman spectroscopy, X-ray diffraction (XRD) patterns and scanning electron microscopy (SEM).
-
-Figure \ref{fig:CDCall}a and b compares the specific capacities of all cells for their first and 50$^{th}$ cycles.
-Human hair cathodes exhibited a high capacity of $\sim$100 mAh g$^{-1}$ with coulombic efficiency of $\sim$95$\%$.
-High surface area due to its porous structure might have led to an additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}.
+Figures \ref{fig:CDCall}a) and b) show the specific capacities of all cells for their first and 50$^{th}$ cycles.
+Human hair cathodes exhibited a high capacity of $\sim$100 mAh g$^{-1}$ with CE of $\sim$95\% shown in Figure \ref{fig:CDCall}c).
 Hemp batteries displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles.
-CFEx displayed a capacity of around 80 mAh g$^{-1}$ with coulombic efficiency of $\sim$90\%.
-With an initial value of 84 mAh g$^{-1}$, specific capacity of SPCB decreased to 47 mAh g$^{-1}$ with a low coulombic efficiency of $\sim$40\%.
-Capacity for SPCB and hemp cells decreased considerably after repeated charge/discharge cycles.
-A low coulombic efficiency (observed in both hemp and SPCB) can be attributed to side reactions in a battery.
-These may include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes_understanding_2015-1}.
-However, capacity fade for CFEx and human hair cells was minimal.
+CFEx displayed a capacity of around 80 mAh g$^{-1}$ with CE of $\sim$90\% and maintained that for 50 cycles.
+With an initial value of 84 mAh g$^{-1}$, specific capacity of Super-P decreased to 47 mAh g$^{-1}$ and a low CE of $\sim$40\% was observed.
+The discharging capacity of SPCB and hemp fibers decreased considerably after repeated charge/discharge cycles.
+A low CE that was observed in both hemp and Super-P, can be attributed to side reactions in the batteries.
+These may include electrode or electrolyte interactions with impurities or degradation of the cathode structure (pulverisation) \cite{gyenes_understanding_2015-1}.
+The capacity loss for CFEx and human hair cells was minimal.
 This suggests that CFEx and human hair have a more stable structure and have the potential to store charge reversibly \cite{pramanick_human_2016}.
 
-% In the above paragraph, you discuss 3 specific cells.
-This is suicidal (metaphorically speaking).
-In science you make a point by showing that something is reproducible.
-Having done just 3 expriments is asking for the reviewer to knock it down.
-You need to re-write this in a more general manner.
-\fbox{\begin{minipage}{46.5em}
 \section*{Activation of carbon}
-The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonised precursor.
-Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas_effect_2004}.
-Using alkali hydroxides at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}.
+The production of AC consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonised precursor.
+Activating agents play an important role in determining the porosity of AC \cite{arenas_effect_2004}.
+Using alkali hydroxides at high temperature creates micropores, which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}.
 In this work, sodium hydroxide (NaOH) was used as the activating agent.
-The reaction that takes place inside the carbon matrix after adding NaOH is as follows:
+The following reaction is taking place within the carbon matrix after addition of NaOH:
 
@@
 
-In this reaction, NaOH was reduced to free metal, Na.
-These atoms in turn expanded the carbon matrix after intercalating into the carbon structure.
-Increased temperature (750$^{\circ}$ C) forced the  atoms out of the carbon matrix, thus creating micropores.
-Oxidation of carbon from oxygen atoms of the hydroxide group formed carbon dioxide (\ce{CO2}), providing routes for channeling the sodium atoms into the internal structure, resulting in a well-connected porous structure \cite{satish_macroporous_2015}.
-The calcinating temperature used here was 750$^{\circ}$ C.
-Figure \ref{fig:ACHsyn} displays a flowchart describing activated carbon synthesis.
-\end{minipage}}
-
-\begin{figure}[ht!]
+\begin{figure}%[ht!]
 \centering
@@
 % Paragraph above: you need to prove/reason every statement that you make. You just claim a lot of stuff without providing any evidence. Also: ARTICLES!!!!!
+Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals (vdW) diameter of 11\AA\ in a single crystal.
+However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}.
+They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}.
+To test their solubility in \ce{AlCl3}-EMImCl, 100 mg of CFEx were mixed in the electrolyte and stirred for 24 hours.
+The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box.
+CFEx seemed to dissolve in the RTIL (Figure \ref{fig:CFExsol}) since no phase separation was observed.
+It has been reported that poly-sulphides (formed during charge/discharge cycles) are soluble in the electrolyte of a Li-S battery.
+They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}.
+Since no such effect was observed in the fullerene cells, this phenomena does not seem to impact its charge-storing capacity.
+On the contrary, Al/CFEx cells demonstrated excellent capacity retention at various current rates (Figure \ref{fig:CDCall}d)).
 
-%Unfortunately the structural domains appeared to have been damaged after this process. This phenomena negatively impacted its charge-storing capacity.
-
-% Above paragraph: Lots of unnecerssary information (see comments).
-Focus on what is relevant.
-Also sentences like the Carbon Valley one are suicidal.
-When you write, always have your worst scientific enemy in mind and write it so that you win.
-\begin{figure}[h!]
+\begin{figure}
 \centering
@@
 
-Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals (vdW) diameter of 11\AA\ in a single crystal.
-However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}.
-They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}.
-To test their solubility in \ce{AlCl3}-EMImCl, 100 mg of CFEx was mixed in the electrolyte and stirred for 24 hours.
-The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box.
-CFEx seemed to dissolve in the RTIL (Figure \ref{fig:CFExsol}) since no phase separation was observed.
-It has been reported that poly-sulphides (formed during charge/discharge cycles) are soluble in the electrolyte of a Li-S battery.
-They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}.
-Since no such effect was observed in aluminium-fullerene cells, the solubility of fullerenes does not seem to impact the charge-storing capacity of CFEx.
-On the contrary, aluminium-fullerene batteries demonstrated excellent capacity retention at various current rates(Figure \ref{fig:CDCall}d).
+It has been previously established that chloroaluminates intercalate into the graphitic planes during charging \cite{lin_ultrafast_2015-2}.
+Since both AC and SPCB cathodes contain graphitic planes, we expected intercalation during cell charging.
+To study these changes, charged cathodes of all materials were analysed by Raman spectroscopy and compared with the pristine ones.
+The data obtained is displayed in Figure \ref{fig:raman}.
+Graphite shows a characteristic D-band present at 1300 cm$^{-1}$, which originates from the hybridized vibrational modes associated with graphene edges and indicates the absence of long-range order.
+Pristine hair, hemp and SPCB cathodes showed a significant D-band present at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB, indicating the absence of a defined lattice structure.
+Both the peaks at 1600 cm$^{-1}$ and 1350 cm$^{-1}$ are broad due to the presence of \ce{sp2} clusters like $\alpha$-carbons, which have a bond angle disorder \cite{shimodaira_raman_2002}.
 
- \begin{figure}[h!]
-  \centering
-  \includegraphics[width=\textwidth]{fig/superPmech}
-    \caption{Suggested mechanism for an aluminium-SPCB cell.
-\ce{AlCl4-} anions intercalate into the very few graphitic planes in Super-P, while few anions adsorb onto its surface.
-However, further cycling leads to cathode pulverisation, which results in capacity fading.}
-  \label{fig:superPmech}
-\end{figure}
-
-Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure.
-The pore sizes range from $\sim$30-50 nm \cite{younesi_analysis_2015}.
-As a cathode material, SPCB underwent the highest capacity loss within 30 cycles (45\%).
-It seems continuous cycling destroyed the structural arrangement of the carbon atoms, which resulted in further alleviated capacity and low coulombic efficiencies.
-
- \begin{figure}[h!]
-  \centering
-  \includegraphics[width=\textwidth]{fig/hempmech}
-    \caption{Suggested mechanism for an aluminum-hemp cell.
-Hemp fibers have pore sizes which might be as large as 2.0-2.5 $\mu$m allowing the \ce{AlCl4-} to get absorbed on their surface.
-However, agglomeration of these fibers after a few cycles reduces the number of active sites available for effective charge storage.}
-  \label{fig:hempmech}
-\end{figure}
-
- \begin{figure}[h!]
+ \begin{figure}
   \centering
   \includegraphics[width=\textwidth]{fig/raman}
-    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx, b) hemp, c) human hair and d) SPCB cathodes displaying presence of both D and G bands.}
+    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx, b) AC from hemp fibers, c) from human hair (ACH) and d) Super-P cathodes displaying presence of both D and G bands.}
   \label{fig:raman}
@@
 
-It has been previously established that chloroaluminates intercalate into the graphitic planes during charging \cite{lin_ultrafast_2015-3}.
-Since activated carbon and SPCB cathodes tested in this work have graphitic planes present in them, we compared the pristine and charged electrodes only.
-Figure \ref{fig:raman} displays the Raman spectra of the pristine and charged (intercalated) cathodes.
-Pristine hair, hemp and SPCB cathodes had a significant D-band present in them, indicating absence of an ordered structure (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB).
-Broad peaks at about 1600 cm$^{-1}$ and about 1350 cm$^{-1}$ arise from \ce{sp2} clusters like $\alpha$-carbons with bond angle disorder \cite{shimo}.
-Raman spectra of CFEx in Figure \ref{fig:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules.
+Raman spectra of CFEx in Figure \ref{fig:raman}c) displayed the characteristic bands of both \ce{C60} and \ce{C70} molecules.
 A 'pentagonal pinch mode', usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$.
-\ce{C70} has multiple bands because it has a reduced molecular symmetry, which increases the number of vibrational modes, consequently increasing the number of active Raman bands \cite{kimbrell_analysis_2014}.
-It was interesting to note that the spectra of charged CFEx looked strikingly similar to the pristine ones, Figure \ref{fig:raman}c.
-Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the fullerenes did not undergo any significant structural change during cycles.
+It was observed that \ce{C70} had multiple bands.
+This was due to its reduced molecular symmetry, which increased the number of vibrational modes, consequently increasing the number of active Raman bands \cite{kimbrell_analysis_2014}.
+It was interesting to note that the spectra of charged CFEx looked almost identical to the pristine ones.
+The results suggested that the fullerenes did not undergo any significant structural change during the cycles.
+As a result, the cells displayed a very stable CE.
+Furthermore, fullerenes stored the same amount of charge after every cycle (similar discharge capacity after 50 cycles) without undergoing any significant structural changes.
+
 Charged AC (from hair) cathodes showed an increased full-width at half maxima (FWHM), which suggested an increase in the lattice defects and structure deformities.
-Obviously, these defects arise after intercalation of chloroaluminates into the few graphitic planes present in the carbon matrix.
-Furthermore, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}.
-Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge \cite{brezesinski_ordered_2010}.
-Schematic of an aluminium-hair battery is illustrated in Figure \ref{fig:ACHmech}.
+These defects would arise if the chloroaluminate ions intercalated into the few graphitic planes present in the carbon matrix.
+However, a highly porous structure would also allow surface adsorption of charge carrying species much like in super-capacitors \cite{beguin_carbons_2014}.
+Since activated carbon lacks the long-range ordered structure present in natural graphite, intercalation into short-range graphitic planes, as well as surface adsorption of chloroaluminates, can contribute to its high capacity \cite{brezesinski_ordered_2010}.
+This might have resulted in aluminium-hair batteries performing better than other materials by storing more charge as a result of the dual mechanism.
+A schematic of the proposed mechanism of an aluminium-hair battery is displayed in Figure \ref{fig:ACHmech}.
 
- \begin{figure}[h!]
+ \begin{figure}%[h!]
   \centering
   \includegraphics[width=\textwidth]{fig/ACHmech}
-    \caption{Suggested mechanism for an aluminium-human hair cell.
-Chloroaluminates (\ce{AlCl4-}) intercalate into the few graphitic planes and micro/mesopores present in them, in addition to surface adsorption of ions displaying both Faradaic and non-Faradaic processes for charge storage.}
+    \caption{Suggested mechanism for an Al/hair cell.
+Chloroaluminate ions (\ce{AlCl4-}) intercalate into the few graphitic planes and micro/mesopores present in them, in addition to surface adsorption of ions displaying both Faradaic and non-Faradaic processes for charge storage.}
   \label{fig:ACHmech}
@@
 %contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.
-Hemp fibers and SPCB had a highly disordered structure to begin with.
-Repeated intercalation or absorption of ions on their surface in the first few cycles would have further increased the lattice defects, which is one of the reasons why hemp and SPCB batteries failed to retain their capacity.
+
+Figure \ref{fig:allmech}b) and c) show the proposed mechanism of charge storage in an Al/hemp and Al/SPCB cell.
+Both hemp fibers and SPCB had a highly disordered structure to begin with (cf.\ Raman spectra).
+Repeated intercalation or adsorption of ions onto their surface during the first few cycles further damaged their structure, which is one of the reasons why hemp and SPCB batteries failed to retain their capacity.
 However, CFEx does not have graphitic planes to intercalate chloroaluminate ions.
 Since the fullerenes have a very high surface area, surface adsorption of ions is highly likely \cite{adams_van_1994}.
-Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes (as shown in Figure \ref{fig:CFExmech}) and for the surface-based redox processes to take place in a systematic way.
+Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes (\ce{C60} and \ce{C70}) as shown in Figure \ref{fig:allmech}a) and for the surface-based redox processes to take place in a systematic way throughout the electrode.
 
- \begin{figure}[tbh!]
+\begin{figure}
   \centering
-  \includegraphics[width=\textwidth]{fig/CFExmech}
-    \caption{Suggested mechanism for a fullerene cell. \ce{AlCl4-} ions seeping in through the gaps present between fullerene molecules.}
-  \label{fig:CFExmech}
+  \includegraphics[width=\textwidth]{fig/allmech}
+    \caption{Suggested mechanism for an a) Al-CFEx cell, b) Al-hemp cell, hemp fibers have pore sizes as large as 2.0-2.5 $\mu$m allowing the \ce{AlCl4-} to get absorbed on their surface.
+However, agglomeration of these fibers after a few cycles reduces the number of active sites available for effective charge storage, and c) Al-Super-P cell, chloroaluminates intercalate into the very few graphitic planes in Super-P, while few anions adsorb onto its surface.
+However, further cycling leads to cathode pulverisation, which results in capacity fading.}
+  \label{fig:allmech}
 \end{figure}
 
-\begin{figure}[h!]
+Figure \ref{fig:SEM} shows the SEM images of pristine (Figure \ref{fig:SEM}a), b), c) and d)) and charged (\ref{fig:SEM}e) ,f) ,g) and h)) cathodes of all carbon materials.
+Human hair and hemp fibers have a highly porous structure as seen in Figure \ref{fig:SEM}b) and d).
+However, hemp lost its surface porosity after 30 cycles, Figure \ref{fig:SEM}f).
+In addition, Figure \ref{fig:SEM}d) and h) implies that SPCB underwent significant agglomeration during cycles.
+It was interesting to note that the fullerene cathode retained its morphology after 50 cycles.
+
+\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{fig/SEM}
-    \caption{Scanning electron microscopy (SEM) images comparing pristine a) human hair, b) hemp, c) CFEx and d) SPCB and charged e)human hair, f) hemp, g) CFEx and h) SPCB cathodes.
+    \caption{Scanning electron microscopy (SEM) images comparing pristine a) human hair, b) hemp, c) CFEx and d) SPCB and charged e) human hair, f) hemp, g) CFEx and h) SPCB cathodes.
 Hemp fibers and SPCB undergo permanent changes after charge/discharge cycles and fail to retain capacity.}
@@
 
-Figure \ref{fig:SEM} shows the SEM images of pristine (Figure \ref{fig:SEM}a, b, c and d) and charged (\ref{fig:SEM}e,f,g and h) cathodes of all carbon materials.
-Activated carbon has a highly porous structure as seen in Figure \ref{fig:SEM}b and d).
-However, hemp cathodes lost their porosity and degraded after 30 cycles, Figure \ref{fig:SEM}f).
-Significant agglomeration was observed in SPCB as well (Figure \ref{fig:SEM}d) and h).
-It was interesting to note that the cycled AC (from hair) and fullerene cathodes did not undergo any significant changes after cycles.
+Pristine (in black), charged (in green) and discharged (in red) cathodes of CFEx and human hair are showed in Figure \ref{fig:XRD}a) and b) respectively.
+Figure \ref{fig:XRD}a) displays the characteristic peaks of both \ce{C60} and \ce{C70} at 2$\theta$ values of 10.9$^{\circ}$, 17.8$^{\circ}$, 20.9$^{\circ}$ and 28.2$^{\circ}$ for \ce{C60} and 18.9$^{\circ}$, 19.3$^{\circ}$ and 21.8$^{\circ}$ for \ce{C70} molecules.
+New diffraction peaks at lower 2$\theta$ values appeared for charged electrodes.
+However, after discharge, the XRD patterns looked similar to the ones of the pristine cathodes.
+This data strongly suggests a reversible process taking place during cycling.
+To confirm this, the unit cell lattice parameters for both pristine and charged cathodes using \ce{C60} were calculated.
+The unit cell had a tetragonal crystal symmetry with a space group of \textit{P42/ mmc} and a space group number 131 (ICDD: 04-013-1339).
+Lattice parameters 'a' and 'b' for the charged cathode increased from 9.06 \AA\ to 9.57 \AA\ and 'c' increased from 15.03 \AA\ to 15.65 \AA, as shown in Figure \ref{fig:cfexcrys}a) and b).
+Lattice parameters of a discharged fullerene were closer to pristine values.
+These changes suggested a reversible insertion of chloroaluminates into the free spaces between fullerene molecules taking place.
+A possible site for \ce{AlCl4-} intercalation is depicted in Figure \ref{fig:cfexcrys}c).
 
-\begin{figure}[h!]
+\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{fig/XRD}
-    \caption{X-ray diffarction patterns of a) CFEx and b)human hair cathodes to study changes in their lattice after galvanostatic cycles in a two-electrode setup against \ce{Al$^{3+}$/Al} with characteristic peaks marked for \ce{C60} (in grey boxes) and \ce{C70} (in blue inverted trainagles).}
+    \caption{X-ray diffraction (XRD) patterns of a) CFEx and b)human hair cathodes to study changes in their lattice after galvanostatic cycles in a two-electrode setup against \ce{Al$^{3+}$/Al} with characteristic peaks marked for \ce{C60} (in grey boxes) and \ce{C70} (in blue inverted triangles).}
   \label{fig:XRD}
@@
 
-To further explore the structural stability and the mechanism in CFEx and hair batteries, X-ray diffraction patterns were examined.
-Pristine (in black), charged (in green) and discharged (in red) cathodes of CFEx and human hair are showed in Figure \ref{fig:XRD}a and b respectively.
-Figure \ref{fig:XRD}a displayed the characteristic peaks of both \ce{C60} and \ce{C70} at 2$\theta$ values of 10.9$^{\circ}$, 17.8$^{\circ}$, 20.9$^{\circ}$ and 28.2$^{\circ}$ for \ce{C60} and 18.9$^{\circ}$, 19.3$^{\circ}$ and 21.8$^{\circ}$ for \ce{C70} molecules.
-New diffraction peaks at lower 2$\theta$ values appeared for charged electrodes.
-However, after discharge, the XRD patterns looked similar to the diffraction peaks of the pristine cathode.
-This data strongly suggests a reversible process taking place during cycles.
-To confirm, we calculated the unit cell lattice parameters for both pristine and charged cathodes for a \ce{C60} molecule.
-The unit cell had a tetragonal crystal system with space group of P42/ mmc and a space group number 131 (ICDD: 04-013-1339).
-Lattice parameters 'a' and 'b' for the charged cathode increased from 9.06 \AA\ to 9.57 \AA\ and 'c' increased from 15.03 \AA\ to 15.65 \AA, as shown in Figure \ref{fig:CFExcryst}a and b.
-Lattice parameters of a discharged fullerene were closer to pristine values.
-These changes suggested a reversible insertion of chloroaluminates into the free spaces between fullerene molecules taking place.
-A possible site for \ce{AlCl4-} intercalation is depicted in Figure \ref{fig:CFExcryst}c.
-XRD patterns of human hair cathodes were inconclusive (Figure \ref{fig:XRD}b).
-Pristine cathode showed broad peaks that demonstrate an amorphous and highly porous structure.
-However, the material became more symmetrical and crystalline after cycles.
-Charged and discharged cathodes exhibited similar looking patterns implying no change in the newly formed crystal lattice during cycles.
-It is to be noted that presence of crystallinity in an active material does not limit the surface-based charge storing capacity \cite{kim_synthesis_2006, jow_factors_2018}.
-
-\begin{figure}[tbh!]
+\begin{figure}%[tbh!]
   \centering
-  \includegraphics[width=\textwidth]{fig/CFExcryst}
+  \includegraphics[width=\textwidth]{fig/cfexcrys}
     \caption{Changes in the lattice parameters of a \ce{C60} unit cell.
@@
 c) Expected intercalation sites of \ce{AlCl4-} ions in the unit cell.}
-  \label{fig:CFExcryst}
+  \label{fig:cfexcrys}
 \end{figure}
 
-%Charged Super-P and hemp fiber electrodes underwent degradation and appeared clumped together resulting in capacity decay.
-This was visible from their electrochemical results where a rapid decrease in capacity and cell efficiency was noted.
+XRD patterns of human hair cathodes were inconclusive (Figure \ref{fig:XRD}b)).
+The pristine cathode displayed broad peaks that confirmed a structure that was amorphous and highly porous.
+However, the material became more symmetrical and crystalline after cycling.
+Charged and discharged cathodes exhibited similar looking patterns implying no change in the newly formed crystal lattice during cycles.
+It has to be noted that the presence of crystallinity in an active material does not limit the surface-based charge storing capacity \cite{kim_synthesis_2006, jow_factors_2018}.
+Further analysis is required to investigate this unique behaviour and establish its mechanism.\\
+To determine the different bonds and environments existing in all the carbon-based cathodes, XPS spectra of the carbon 1s orbital of all pristine cathodes is shown in Figure \ref{fig:XPSC}.
+Hair, hemp fibers and SPCB had similar looking peaks for the 1s orbital.
+All three cathodes displayed peaks for sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds.
+Since hair is mainly composed of a protein called keratin (Figure \ref{fig:keratin}), it can be deduced that multiple chemical environments of carbon, shown in Figure \ref{fig:XPSC}a), are derived from Keratin.
+Sulphide bonds are an essential part of this protein and a C-S binding energy was observed at 286.94 eV (blue peak).
 
-%XPS analysis results... C 1s 
-\begin{figure}[tbh!]
+\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{fig/XPSC}
-    \caption{Carbon 1s XPS spectra of pristine a) ACH, b) Super-P, c) hemp fibers and d) CFEx cathodes.While ACH, Super-P and hemp fibers observe carbonyl functional groups, CFEx cathodes have symmetrical looking $\pi$* and $\sigma$* satellite peaks.}
+    \caption{Carbon 1s XPS spectra of pristine a) hair, b) Super-P, c) hemp fibers and d) CFEx cathodes.
+While AC from human hair (ACH), hemp fibers and Super-P contain carbonyl functional groups, CFEx cathodes have symmetrical looking $\pi$* and $\sigma$* satellite peaks.}
   \label{fig:XPSC}
-\end{figure}
-
-XPS spectra of carbon 1s orbital of all pristine cathodes is shown in Figure \ref{fig:XPSC}.
-Hair, hemp fibers and SPCB had similar looking peaks for the 1s orbital.
-All three cathodes displayed peaks for sp$^2$ C-C/ C-H, C-O/ C-OH, O-C=O/ C=O and C-F bonds .
-Since hair is mainly composed of a protein called keratin (Figure \ref{fig:keratin}), it can be deduced that multiple chemical environments of carbon, shown in Figure \ref{fig:XPSC}a), are derived from Keratin.
-Sulphide bonds are an essential part of this protein and a C-S binding energy is observed at 286.94 eV (blue peak).
-
-\begin{figure}[th!]
-\centering
-\includegraphics[width=0.5\textwidth]{fig/keratin}
-\caption{Keratin: a protein abundantly found in human hair contains C-O, C=O, C-NH$_2$ bonds.}
-\label{fig:keratin}
 \end{figure}
@@
 
-Functional groups that contain oxygen, such as carbonyl and ester groups, improve the wettability of a material, which increases the availability of active surface area \cite{younesi_analysis_2015}.
-SPCB is produced from partial oxidation of petrochemical precursors \cite{gnanamuthu_electrochemical_2011}.
+Functional groups that contain oxygen, such as carbonyl and ester groups, improve the wettability of a material.
+This increases the availability of the active surface area as more electrolyte ions can interact with the material's surface \cite{younesi_analysis_2015}.
+SPCB is produced by partial oxidation of petrochemical precursors \cite{gnanamuthu_electrochemical_2011}.
 A perfect graphite surface containing only carbon atoms, without heteroatoms like oxygen and sulfur, would give a very well-ordered structure.
-Presence of impurities such as carbonyl groups creates defects resulting in a less graphitic and more amorphous structure\cite{hao_carbonaceous_2013} and peaks at 288.0 eV in AC and SPCB cathodes confirm that.
-Spectra for C 1s orbital of CFEx was uniquely different than the others due to presence of several highly symmetrical peaks.
-The presence of $\pi$ electrons on its surface results in  multiple $\pi$ satellite peaks, which are typical in a \ce{C60} molecule \cite{skryleva_xps_2016}.
+The presence of impurities such as carbonyl groups creates defects resulting in a less graphitic and more amorphous structure \cite{hao_carbonaceous_2013} and peaks at 288.0 eV for -CO bonds in AC and SPCB cathodes confirming this observation.
+The presence of these defects was also observed in the form of D-bands in their Raman spectra (Figure \ref{fig:raman}).
+However, spectra for the C 1s orbital of CFEx were uniquely different due to the presence of several highly symmetrical peaks.
+The presence of $\pi$ electrons on its surface resulted in  multiple $\pi$ satellite peaks, which are typical in a \ce{C60} molecule \cite{skryleva_xps_2016}.
 These peaks appear in both high (in green) and low energy ranges (in red) \cite{erbahar_spectromicroscopy_2016, poirier_carbon_1993}.
-%Existence of several peaks in the $\pi$ satellite of a C$_6_0$ molecule is caused by the angular quantisation of orbitals around the centre of the spherical molecule. 
-%XPS analysis results... O 1s
 
-\begin{figure}[h!]
+Figure \ref{fig:XPSON}a)-d) shows various binding energies for the oxygen 1s orbital.
+In addition to enhancing the wettability of a material \cite{li_effect_2011, oh_oxygen_2014}, oxygen-containing surface functional groups can provide pseudo-capacitance by reacting with electrolyte ions \cite{bleda-martinez_role_2005}.
+This might be another reason why aluminium-hair batteries performed better than the others.
+Due to its enhanced wettability, the active material was more exposed to the chloroaluminate ions.
+Figure \ref{fig:XPSoverall} displays the overall spectra of all tested cathodes.
+Table \ref{table1} summarises all the functional groups with their respective binding energies for all tested cathode materials in this project.
+
+\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{fig/XPSON}
-    \caption{XPS spectra of O 1s orbital for a) human hair, b) hemp fibers c) CFEx and d) SPCB cathodes.
+    \caption{XPS spectra of O 1s orbital for a) AC from human hair (ACH), b) hemp fibers c) CFEx and d) SPCB cathodes.
 Hair and hemp fibers contained significant amounts of aliphatic (red) and aromatic (pink) C=O groups  compared to CFEx and SPCB.
@@
 
-Figure \ref{fig:XPSON}a-d shows various binding energies for O 1s orbital.
-In addition to enhancing the wettability of a material, oxygen containing functional groups make redox reactions feasible \cite{li_effect_2011, oh_oxygen_2014}.
-Oxygen-containing surface functional groups can provide pseudo-capacitance by reacting with electrolyte ions \cite{bleda-martinez_role_2005}.
-This might another reason why aluminium-hair batteries performed better than the others.
-Figure \ref{fig:XPSoverall} displays the overall spectra of all tested cathodes.
-Table \ref{table2} compiles all the functional groups with their respective binding energies for all tested cathode materials in this work.
-
-\begin{figure}[th!]
+\begin{figure}%[th!]
 \centering
@@
 
- \begin{figure}[h!]
+\begin{table}
+\caption{Comparing battery metrics of all carbon-based cathodes tested in this work} \label{table1}
+\begin{center}
+\begin{tabular}{|lccc|}
+\hline
+Active material  & {\textbf{Specific capacity}} & {\textbf{Cell efficiency}} & {\textbf{Cell voltage}}\\
+ & {\textbf{(mAh g$^{-1}$)}} & {\textbf{(\%)}} & {\textbf{(V)}}\\
+\hline
+Human hair &  102 & 97 & 1.9 \\
+Fullerene mix &  78 & 85 & 1.7 \\
+Hemp fibers & 49 & 75 & 1.8 \\
+SPCB & 46 & 40 & 1.5 \\
+\hline  
+\end{tabular}
+\end{center}
+\end{table}
+
+Lastly, to confirm whether AC derived from human hair is a psedocapacitive material, cyclic voltammograms of all cathodes at a scan rate of 10 mV s$^{-1}$ were compared.
+Figure \ref{fig:CV}a)-e) showed that human hair batteries resulted in a more rectangular, capacitor-like CV curve.
+However, redox processes were noticeable at a scan rate of 10 mV s$^{-1}$ and tiny redox peaks were visible in Figure \ref{fig:CV}b) at 1.8 and 2.1 V during charging and 1.1 and 1.9 V during discharge.
+At a higher scan rate (50 mV s$^{-1}$), the redox peaks disappeared and the material displayed an ideal capacitor-like CV curve, shown in Figure \ref{fig:hair50mVs} \cite{guan_capacitive_2016, dupont_separating_2015}.
+This happens because at a higher scan rate, the diffusion layer forms very close to the electrode and as a result of which higher current is recorded hiding the redox peaks.
+Although redox peaks were observed for CFEx (at 1.8 V during charging and 1.5 during discharging, which corresponds to the discharging plateau at $\sim$1.5 V) and others (Super-P: 1.8 V during charge and 1.9 and 0.9 V during discharge, hemp fibres: 1.1, 1.2 and 0.8 v during charge and 1.98 and 0.38 V during discharge), the measured current for the Super-P and hemp fibres was very low (negligible compared to human hair).
+At such low currents, it becomes impossible to draw conclusions about the reduction/oxidation reactions taking place and the stability of the species resulting from the electron transfer.
+
+ \begin{figure}
   \centering
   \includegraphics[width=\textwidth]{fig/CV}
-    \caption{Cyclic voltammograms of a) CFEx, b) ACH, c) Super-P and d) hemp fibers cathodes at a scan rate of 10 mV s$^{-1}$ against \ce{Al3+}/Al as a counter/reference electrode in a two-electrode setup.
-ACH cathode observed a larger CV area than other cathodes, which comes from an additional pseudocapacitance, adding capacity to the system.}
+    \caption{Cyclic voltammograms of a) CFEx, b) AC from hair, c) Super-P and d) hemp fibers cathodes at a scan rate of 10 mV s$^{-1}$ against \ce{Al3+}/Al as a counter/reference electrode in a two-electrode setup.
+ACH (activated carbon from hair) cathode observed a larger CV area than other cathodes, which comes from an additional pseudocapacitance, adding capacity to the system.}
   \label{fig:CV}
@@
 
-Lastly, to confirm that AC derived from human hair is in fact a psedocapacitive material, we compared cyclic voltammograms of all cathodes at a scan rate of 10 mV s$^{-1}$.
-Figure \ref{fig:CV}a-e showed that human hair batteries demonstrated a more rectangular, capacitor-like CV curve.
-However, redox processes were noticeable at a scan rate of 10 mV s$^{-1}$ and tiny redox peaks were visible (Figure \ref{fig:CV}b).
-At a higher scan rate (50 mV s$^{-1}$), the redox peaks disappeared and the material displayed an ideal capacitor-like CV curve, shown in Figure \ref{fig:hair50mVs} \cite{guan_capacitive_2016, dupont_separating_2015}.
-
-\begin{figure}[th!]
+\begin{figure}%[th!]
 \centering
 \includegraphics[width=\textwidth]{fig/hair50mVs}
-\caption{Cyclic voltammogram of ACH at a scan rate of 50 mV/s in a two electrode setup against \ce{Al3+}/Al showing a capacitor-like behaviour with no visible oxidation-reduction peaks unlike Figure \ref{fig:CV}b where we distinctly observed redox peaks.}
+\caption{Cyclic voltammogram of ACH at a scan rate of 50 mV/s in a two electrode setup against \ce{Al3+}/Al showing a capacitor-like behaviour with no visible oxidation-reduction peaks unlike Figure \ref{fig:CV}b, where redox peaks were observed.}
 \label{fig:hair50mVs}
@@
 
-\begin{figure}[h!]
+\newpage
+\section{Conclusion}
+In summary, AC derived from human hair proved to be the best carbon-based cathode among all the tested materials in this work, with a specific capacity of 100 mAh g$^{-1}$ at a potential of 1.9 V with a CE of $\sim$90$\%$.
+Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers.
+It was found that in CFEx \ce{AlCl4-} anions migrate in and out of the gaps in between the fullerenes changing its structure and slightly expanding the crystal lattice during charging (Figure \ref{fig:cfexcrys}).
+Moreover, fullerenes maintain their structural integrity and CE throughout the cycles.
+Hemp fibers and Super-P on the other hand, have a highly amorphous structure, which degraded after every cycle, resulting in a low capacity value.
+Figure \ref{fig:CFExACHlong} shows the 50th cycle measurement for Al/hair and Al/natural graphite cell.
+It not only displays a higher specific capacity than conventional graphite, but also a high battery voltage of 1.92 V with an energy density of 202 Wh kg$^{-1}$.
+The high battery performance can be attributed to the porosity of the material combined with its high surface area and the presence of hetero-atoms.
+The cumulative effect of the surface-based non-Faradaic and redox Faradaic contributions lead to the material achieving higher capacities than the other materials.
+
+\begin{figure}%[h!]
   \centering
   \includegraphics[width=\textwidth]{fig/CFExACHlong}
-    \caption{Discharge capacities of a) ACH and b) CFEx cathodes at current rates of 50mAg$^{-1}$, 500mAg$^{-1}$, 1.0 Ag$^{-1}$ and 1.5 Ag$^{-1}$ along with their coulombic efficiencies. }
+    \caption{Discharge capacities of a) ACH and b) CFEx cathodes at current rates of 50 mAg$^{-1}$, 500 mAg$^{-1}$, 1.0 Ag$^{-1}$ and 1.5 Ag$^{-1}$ along with their CEs. }
   \label{fig:CFExACHlong}
 \end{figure}
-
-\newpage
-% Are the following the conclusions?
-\section{Conclusion}
-In summary, AC derived from human hair proved to be the best carbon-based cathode among all the tested materials in this work, with a specific capacity of 100 mAh g$^{-1}$ at a potential of 1.9 V with a coulombic efficiency of $\sim$90$\%$.
-Intercalation and deintercalation of \ce{AlCl4-} takes place in the very few graphitic layers.
-We found that in CFEx \ce{AlCl4-} anions seep in and out of the gaps in between the fullerenes changing its structure and slightly expanding the crystal lattice during charging(Figure \ref{fig:CFExmech}).
-Moreover, fullerenes maintains their structural integrity and coulombic efficiency throughout the cycles.
-Hemp fibers and Super-P on the other hand, have a highly amorphous structure, which degraded after every cycle, resulting in a low capacity value.
-Figure \ref{fig:CFExACHlong} compares the 50th cycle measurement for Al/hair and Al/natural graphite cell.
-It not only displays a higher specific capacity than conventional graphite, but also a high battery voltage of 1.92 V with an energy density of 202 Wh kg$^{-1}$.
-The high battery performance can be attributed to the porosity of the material combined with high surface area and hetero-atom doping effects, combining surface-based non-Faradaic and Faradaic contributions.
-Hair based aluminium-ion batteries would not only be cheaper than state of the art, but would also be one of its kind bio-degradable materials in the battery industry.
 
@@
 \subsection{Chemicals}
-\subsubsection*{Activated carbon from human hair}
+\subsubsection*{AC from human hair}
+AC derived from human hair was prepared by obtaining hair from the barber shops located in Wellington.
+The hair was initially cut into small pieces and washed thoroughly using isopropanol (IPA) to get rid of any chemicals from shampoo and conditioners.
+The samples were then dried at 100 $^{\circ}$C for 12 hours.
+The dried hair was then burnt in Ar atmosphere at 300 $^{\circ}$C for 90 minutes.
+The pre–carbonized sample was then mixed with NaOH (Sigma-Aldrich) in a mass ratio of 1:2.
+The sample was later carbonized at 750 $^{\circ}$C for 3 hours in presence of Ar.
+The product obtained was repeatedly washed with hot milli-q water to remove any traces of sodium from the sample, which was then dried at 80 $^{\circ}$C for 6 hours to obtain the final product.
 
-\subsubsection*{Activated carbon from hemp fibers}
+\subsubsection*{AC from hemp fibers}
 The material was provided by Carbon Valley and used as received.
 \subsubsection*{Fullerene extract}
-C60/C70, approx. 85\% \ce{C60}, 14\% \ce{C70}, and 1\% higher fullerenes, was purchased from SES research and used as received.
+\ce{C60}/\ce{C70}, approx. 85\% \ce{C60}, 14\% \ce{C70}, and 1\% higher fullerenes, was purchased from SES research and used as received.
 \subsubsection*{Super-P carbon black}
-Super-P conductive carbon, 99+\% metals basis was purchased from Alfa-Aesar and used as received
+Super-P conductive carbon, 99+\% metals basis was purchased from Alfa Aesar and used as received
 
@@
 A slurry was prepared by mixing the active material (85$\%$ by wt.), 9$\%$ binder (PVDF, MTI Corp.) and 6$\%$ Super-P conductive carbon (99+$\%$ metals basis, Alfa Aesar) in N-methyl pyrrolidone NMP (anhydrous, 99.5$\%$, Sigma-Aldrich).
-For SPCB slurry 94$\%$ active material and 6$\%$ binder was mixed together to form a slurry.
-It was ‘doctor-bladed’ on molybdenum foil used as a conductive substrate (thickness 0.1 mm, MTI Corp.) and dried in a vacuum oven at 120$^{\circ}$C for 12 hours to adhere the slurry on the substrate and evaporate the solvent.
-Specific loading of the materials ranged from 11-12 mg cm$^{-2}$.
+To form the Super-P slurry, 94$\%$ (by weight) of Super-P (active material) and 6$\%$ (by weight) of the binder were mixed together in the solvent.
+The slurries was then doctor-bladed onto molybdenum foil, which was used as the current collector (thickness 0.1 mm, MTI Corp.).
+The coated sheets were dried in a vacuum oven at 120$^{\circ}$C for 12 hours to adhere the slurry on the substrate and fully evaporate the solvent.
+The specific loading of the slurry material ranged from 11-12 mg cm$^{-2}$ on each cathode.
 
@@
 80$\mu$l of the electrolyte was used to wet the separator.
-Aluminium foil (thickness 0.1 mm, 99$\%$, GoodFellow) used as an anode and placed on top of the separator.
+Al foil (thickness 0.1 mm, 99$\%$, GoodFellow) used as an anode and placed on top of the separator.
 It was assembled in a N$_2$-filled glove box.
 The cell was then sealed and wrapped with a paraffin film to avoid any air or moisture contact.
-Since this was a two-electrode setup, aluminium foil was used as both counter and reference electrode.
+Since this was a two-electrode setup, Al foil was used as both counter and reference electrode.
 The cell was taken out of the glove box and electrochemical measurements were performed.
 
-\begin{figure}[th!]
-\centering
-\includegraphics[width=0.5\textwidth]{fig/PEEK}
-\caption{A custom-made two-electrode polyetherether ketone (PEEK) cell used for galvanostatic cycles and cyclic voltammetry.}
-\label{fig:PEEK}
-\end{figure}
+\subsection{Activation of carbon (hair)}
+In this reaction, NaOH was reduced to free metal, Na.
+These atoms in turn expanded the carbon matrix after intercalating into the carbon structure.
+Increased temperature (750$^{\circ}$ C) forced the  atoms out of the carbon matrix, thus creating micropores.
+Oxidation of carbon from oxygen atoms of the hydroxide group formed carbon dioxide (\ce{CO2}), providing routes for channeling the sodium atoms into the internal structure, resulting in a well-connected porous structure \cite{satish_macroporous_2015}.
+The calcinating temperature used here was 750$^{\circ}$ C.
+Figure \ref{fig:ACHsyn} displays a flowchart describing an AC synthesis.
+
+\section{Acknowledgement}
+We thank Panya Thanwisai and Dr. Nonglak Meethong from Khong Kaen University, Thailand for their help with the synthesis of AC from human hair.
 
